---
title: "geom_pop() Examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{geom_pop() Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  fig.width  = 7,
  fig.height = 5,
  dpi = 100,
  out.width = "100%"
)
```

```{r load}
library(ggpop)
library(ggplot2)
library(dplyr)
```

---

## Example 1: Population by Sex

A simple two-group population chart using Mexico's 2024 population data.

```{r sex}
df_sex <- data.frame(
  sex = c("male", "female"),
  n   = c(63459580, 67401427)
)

df_sex_proc <- process_data(
  data        = df_sex,
  group_var   = sex,
  sum_var     = n,
  sample_size = 100
) %>%
  mutate(icon = case_when(
    type == "male"   ~ "male",
    type == "female" ~ "female"
  ))

ggplot() +
  geom_pop(
    data         = df_sex_proc,
    aes(icon = icon, color = type),
    size         = 2,
    dpi          = 100,
    legend_icons = TRUE
  ) +
  scale_color_manual(values = c("male" = "#1E88E5", "female" = "#D81B60")) +
  scale_legend_icon(size = 5) +
  theme_pop() +
  labs(
    title    = "Mexico Population by Sex (2024)",
    subtitle = "Each icon represents ~1% of the total population",
    color    = "Sex"
  )
```

---

## Example 2: Health Status

A three-group chart showing a simulated patient population broken down by health status.

```{r health}
df_health <- data.frame(
  status = c(rep("Healthy", 70), rep("At Risk", 20), rep("Ill", 10)),
  icon   = c(rep("person", 70), rep("person-half-dress", 20), rep("bed-pulse", 10))
)

df_health$status <- factor(df_health$status,
  levels = c("Healthy", "At Risk", "Ill"))

ggplot() +
  geom_pop(
    data         = df_health,
    aes(icon = icon, color = status),
    size         = 2,
    dpi          = 100,
    legend_icons = TRUE
  ) +
  scale_color_manual(values = c(
    "Healthy"  = "#43A047",
    "At Risk"  = "#FFB300",
    "Ill"      = "#E53935"
  )) +
  scale_legend_icon(size = 5) +
  theme_pop() +
  labs(
    title    = "Simulated Patient Population (n = 100)",
    subtitle = "Each icon represents one patient",
    color    = "Status"
  )
```

---

## Example 3: Education Levels

Population chart showing education attainment across four levels.

```{r education}
df_edu <- data.frame(
  level = c("No Schooling", "Primary", "Secondary", "University"),
  n     = c(8, 22, 42, 28)
)

df_edu_proc <- process_data(
  data        = df_edu,
  group_var   = level,
  sum_var     = n,
  sample_size = 100
) %>%
  mutate(icon = "user")

df_edu_proc$type <- factor(df_edu_proc$type,
  levels = c("No Schooling", "Primary", "Secondary", "University"))

ggplot() +
  geom_pop(
    data         = df_edu_proc,
    aes(icon = icon, color = type),
    size         = 2,
    dpi          = 100,
    legend_icons = TRUE
  ) +
  scale_color_manual(values = c(
    "No Schooling" = "#EF5350",
    "Primary"      = "#FFB74D",
    "Secondary"    = "#42A5F5",
    "University"   = "#66BB6A"
  )) +
  scale_legend_icon(size = 5) +
  theme_pop() +
  labs(
    title    = "Education Attainment",
    subtitle = "Each icon represents 1% of the population",
    color    = "Level"
  )
```

---

## Example 4: Disease Burden with Dark Theme

A dark-themed chart showing disease categories in a simulated population.

```{r disease-dark}
df_disease <- data.frame(
  condition = c(rep("Cardiovascular", 32), rep("Cancer", 18),
                rep("Respiratory", 14), rep("Diabetes", 12),
                rep("Other", 24)),
  icon      = c(rep("heart-pulse", 32), rep("ribbon", 18),
                rep("lungs", 14), rep("syringe", 12),
                rep("user", 24))
)

df_disease$condition <- factor(df_disease$condition,
  levels = c("Cardiovascular", "Cancer", "Respiratory", "Diabetes", "Other"))

ggplot() +
  geom_pop(
    data         = df_disease,
    aes(icon = icon, color = condition),
    size         = 2,
    dpi          = 100,
    legend_icons = TRUE
  ) +
  scale_color_manual(values = c(
    "Cardiovascular" = "#EF5350",
    "Cancer"         = "#AB47BC",
    "Respiratory"    = "#42A5F5",
    "Diabetes"       = "#FFB74D",
    "Other"          = "#78909C"
  )) +
  scale_legend_icon(size = 5) +
  theme_pop_dark(bg_color = "#0D1B2A", text_color = "white") +
  labs(
    title    = "Disease Burden by Condition",
    subtitle = "Simulated population of 100 individuals",
    color    = "Condition"
  )
```

---

## Example 5: Disability Status with Stroke

Using `stroke_width` to outline icons for better visibility and `arrange = TRUE` to group icons by type.

```{r disability}
df_disability <- data.frame(
  sex      = c("male", "female", "disabled males", "disabled females"),
  n        = c(46, 44, 5, 5)
)

df_disability_proc <- process_data(
  data        = df_disability,
  group_var   = sex,
  sum_var     = n,
  sample_size = 100
) %>%
  mutate(icon = case_when(
    type == "male"             ~ "male",
    type == "female"           ~ "female",
    type == "disabled males"   ~ "person-cane",
    type == "disabled females" ~ "person-cane"
  ))

ggplot() +
  geom_pop(
    data         = df_disability_proc,
    aes(icon = icon, color = type),
    size         = 2,
    dpi          = 100,
    arrange      = TRUE,
    legend_icons = TRUE,
    stroke_width = 6
  ) +
  scale_color_manual(
    values = c(
      "male"             = "#1565C0",
      "female"           = "#AD1457",
      "disabled males"   = "#0288D1",
      "disabled females" = "#F48FB1"
    )
  ) +
  scale_legend_icon(size = 5) +
  theme_pop() +
  labs(
    title    = "Population by Sex and Disability Status",
    subtitle = "Icons outlined with stroke_width = 6",
    color    = "Group"
  )
```
