---
title: "Finding Icons with fa_icons()"
format:
  html:
    code-fold: false
    code-summary: "Show the code"
vignette: >
  %\VignetteIndexEntry{Finding Icons with fa_icons()}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

## What is `fa_icons()`?
<div style="line-height: 0.6;"><br></div>

`fa_icons()` is a wrapper functions from fontawesome that lets you search and browse the Font Awesome icons available for use in `geom_pop()` and `geom_icon_point()`. Instead of looking for the icon, you can filter by keyword, category, or regular expression and get back a tidy tibble — or a plain character vector — ready to use in your plot code.

```{r}
#| label: load
#| message: false
#| warning: false
#| echo: false
library(ggpop)
library(ggplot2)
library(dplyr)
```

<div style="line-height: 0.6;"><br></div>

---

## Listing All Icons
<div style="line-height: 0.6;"><br></div>

Called with no arguments, `fa_icons()` returns every available Font Awesome icon with its primary semantic category.

```{r}
#| label: all-icons
fa_icons()
```

Each row contains:

| Column | Description |
|:---|:---|
| `icon` | Icon name to pass to `geom_pop()` / `geom_icon_point()` |
| `primary_class` | The first matching semantic category, or `NA` if unclassified |

<div style="line-height: 0.6;"><br></div>

---

## Searching by Name
<div style="line-height: 0.6;"><br></div>

Pass a string to `query` to filter icons whose names contain that substring.

```{r}
#| label: query-fixed
fa_icons(query = "person")
```

```{r}
#| label: query-heart
fa_icons(query = "heart")
```

<div style="line-height: 0.6;"><br></div>

---

## Regex Search
<div style="line-height: 0.6;"><br></div>

Set `regex = TRUE` to use a Perl-compatible regular expression instead of a fixed string.

```{r}
#| label: regex-arrow
# All icons whose name starts with "arrow"
fa_icons(query = "^arrow", regex = TRUE)
```

```{r}
#| label: regex-alternation
# Exact match for two specific icons
fa_icons(query = "^(star|circle)$", regex = TRUE)
```

<div style="line-height: 0.6;"><br></div>

---

## Filtering by Category
<div style="line-height: 0.6;"><br></div>

Use `category` to return only icons that belong to a semantic group.

```{r}
#| label: category
fa_icons(category = "people_users")
```

Combine `query` and `category` to narrow results further.

```{r}
#| label: query-and-category
fa_icons(query = "person", category = "people_users")
```

<div style="line-height: 0.6;"><br></div>

---

## Quick Vector Lookup
<div style="line-height: 0.6;"><br></div>

Set `as_vector = TRUE` to skip the tibble and get a plain sorted character vector. This is the fastest way to browse names or pipe them into other code.

```{r}
#| label: as-vector
fa_icons(query = "house", as_vector = TRUE)
```

```{r}
#| label: as-vector-category
fa_icons(category = "animals", as_vector = TRUE)
```

<div style="line-height: 0.6;"><br></div>

---

## Showing All Classes
<div style="line-height: 0.6;"><br></div>

By default only `primary_class` is returned. Set `primary_only = FALSE` to also get the `all_classes` list-column, showing every category each icon matches.

```{r}
#| label: all-classes
fa_icons(query = "heart", primary_only = FALSE)
```

<div style="line-height: 0.6;"><br></div>

---

## Hiding Unclassified Icons
<div style="line-height: 0.6;"><br></div>

Some icons do not match any category. Set `include_unclassified = FALSE` to drop them.

```{r}
#| label: classified-only
fa_icons(query = "user", include_unclassified = FALSE)
```

<div style="line-height: 0.6;"><br></div>

---

## Using a Custom Class Map
<div style="line-height: 0.6;"><br></div>

Supply your own named list of `category = regex` pairs to `class_map` for domain-specific classification.

```{r}
#| label: custom-map
my_map <- list(
  health   = "^(heart|lungs|brain|virus|syringe|stethoscope|bandage|dna)(-|$)",
  mobility = "^(wheelchair|person-walking|bicycle|car|bus)(-|$)"
)

fa_icons(class_map = my_map, include_unclassified = FALSE)
```

<div style="line-height: 0.6;"><br></div>

---

## From Discovery to Plot
<div style="line-height: 0.6;"><br></div>

A common workflow: search for icons, pick ones you like, then put them directly into a geom.

```{r}
#| label: workflow-search
# 1. Find candidate icons
fa_icons(query = "person", category = "people_users", as_vector = TRUE)
```

```{r}
#| label: workflow-plot
#| message: false
#| fig-width: 10
#| fig-height: 10
#| code-fold: true
#| dev: png
#| dev-args: !expr list(bg = "transparent")

# 2. Use the chosen icons in a population chart
df_pop <- data.frame(
  status = c(rep("Healthy", 70), rep("At Risk", 30)),
  icon   = c(rep("person", 70), rep("person-half-dress", 30))
)

ggplot() +
  geom_pop(
    data = df_pop,
    aes(icon = icon, color = status),
    size = 2.5, dpi = 100, legend_icons = TRUE
  ) +
  scale_color_manual(values = c(
    "Healthy"  = "#43A047",
    "At Risk"  = "#FFB300"
  )) +
  theme_pop() +
  scale_legend_icon(size = 8) +
  labs(
    title    = "Simulated Patient Population (n = 100)",
    subtitle = "Each icon represents one person",
    color    = "Status"
  ) +
  theme(
    plot.title = element_text(size = 16, face = "bold", color="white"),
    plot.subtitle = element_text(size = 12, color="white"),
    legend.position = "bottom",
    legend.text = element_text(size = 12, color="white"),
    legend.title = element_text(size = 14, face = "bold", color="white"))
```

<div style="line-height: 0.6;"><br></div>

---

## Parameter Reference
<div style="line-height: 0.6;"><br></div>

| Parameter | Default | Description |
|:---|:---|:---|
| `query` | `NULL` | Fixed string or regex to filter icon names |
| `category` | `NULL` | One or more category names to filter by |
| `regex` | `FALSE` | Treat `query` as a Perl-compatible regular expression |
| `classify` | `TRUE` | Add a `primary_class` column to the output |
| `include_unclassified` | `TRUE` | Keep icons with no matching category (`NA`) |
| `class_map` | internal | Named list mapping category labels to regex patterns |
| `primary_only` | `TRUE` | Return only `primary_class`; set `FALSE` to add `all_classes` |
| `as_vector` | `FALSE` | Return a plain sorted character vector instead of a tibble |

<div style="line-height: 0.6;"><br></div>

---

## Icon Gallery by Category
<div style="line-height: 0.6;"><br></div>

The gallery below lets you identify every available icon in fontawesome package. Each category is drawn as a `geom_pop()` chart — one icon per type — with the legend showing the actual icon image alongside its name. All icons within a category share a single colour. Pick the ones you like the most for your analysis.

```{r}
#| label: gallery-setup
#| message: false
#| warning: false
#| echo: FALSE

# All classified icons
df_all <- fa_icons(include_unclassified = FALSE)

# One colour per category — semantically grouped
# Optimized for background: #01394f (deep teal/navy)
category_colours <- c(
  # People & Accessibility
  people_users        = "#4FC3F7",  # Light cyan blue
  faces_emotions      = "#FFD54F",  # Warm yellow
  hands_arms          = "#81D4FA",  # Sky blue
  accessibility       = "#64B5F6",  # Medium blue
  gender_identity     = "#B39DDB",  # Soft purple
  people_social       = "#9FA8DA",  # Periwinkle
  
  # UI & Navigation
  ui_navigation       = "#CE93D8",  # Light purple
  ui_actions          = "#E1BEE7",  # Pale purple
  ui_controls         = "#BA68C8",  # Medium purple
  text_formatting     = "#AB47BC",  # Deep purple
  arrows_directional  = "#EA80FC",  # Bright purple
  arrows_extra        = "#F48FB1",  # Pink
  location_navigation = "#FF6090",  # Coral pink
  
  # Files & Data
  files_folders       = "#90A4AE",  # Blue grey
  office_docs         = "#B0BEC5",  # Light blue grey
  charts_analytics    = "#78909C",  # Medium grey blue
  
  # Communication & Technology
  communication       = "#4DD0E1",  # Cyan
  media_controls      = "#26C6DA",  # Dark cyan
  devices_hardware    = "#00ACC1",  # Deep cyan
  tech_science        = "#80DEEA",  # Pale cyan
  
  # Security
  security_privacy    = "#A7FFEB",  # Mint green
  
  # Money & Shopping
  money_currency      = "#66BB6A",  # Green
  shopping_commerce   = "#81C784",  # Light green
  
  # Medical & Emergency
  medical_health      = "#EF5350",  # Red
  medical_extra       = "#E57373",  # Light red
  emergency_hazards   = "#FF7043",  # Orange red
  
  # Transport & Travel
  transport_ground    = "#9575CD",  # Medium purple
  transport_air_sea   = "#B39DDB",  # Light purple
  travel_places       = "#D1C4E9",  # Pale lavender
  transport_extra     = "#7E57C2",  # Deep purple
  
  # Buildings & Places
  buildings_places    = "#A1887F",  # Warm grey
  government_law      = "#BCAAA4",  # Light brown
  buildings_extra     = "#D7CCC8",  # Pale brown
  
  # Religion
  religion_symbols    = "#FFB74D",  # Orange
  religion_extra      = "#FFCC80",  # Light orange
  
  # Food, Home & Household
  food_drink          = "#FF9800",  # Orange
  household           = "#FFB74D",  # Light orange
  food_extra          = "#FFCC80",  # Pale orange
  
  # Nature & Environment
  nature              = "#66BB6A",  # Green
  weather             = "#4FC3F7",  # Sky blue
  nature_extra        = "#AED581",  # Light lime
  
  # Animals
  animals             = "#A1887F",  # Tan
  
  # Sports, Games & Hobbies
  sports              = "#26A69A",  # Teal
  games_hobbies       = "#4DB6AC",  # Light teal
  
  # Tools & Industry
  tools_construction  = "#A1887F",  # Brown grey
  industry_energy     = "#8D6E63",  # Deep brown
  
  # Time & Symbols
  time                = "#7986CB",  # Indigo
  shapes_symbols      = "#9FA8DA",  # Light indigo
  
  # Clothing
  clothing            = "#F06292",  # Pink
  
  # Entertainment
  entertainment       = "#EC407A",  # Hot pink
  
  # Packaging & Objects
  packaging           = "#DCE775",  # Lime yellow
  objects_misc        = "#D4E157",  # Chartreuse
  
  # Alphanumeric
  alphanumeric        = "#CFD8DC",  # Light grey
  
  # Brands
  brands_social       = "#42A5F5",  # Blue
  brands_dev_cloud    = "#26A69A",  # Teal
  brands_commerce     = "#FF7043",  # Coral
  brands_misc         = "#AB47BC"   # Purple
)

```


### People & Accessibility

```{r}
#| label: gallery-people-users
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "people_users")  %>% 
  dplyr::mutate(type = icon)%>% 
  #Get last 42 icons
  dplyr::slice_tail(n = 42)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["people_users"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["people_users"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: people users", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),         
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))

```


#### People Users

```{r}
#| label: gallery-people-users-2
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "people_users")  %>% 
  dplyr::mutate(type = icon) %>% 
  #Get first 42 icons
  dplyr::slice_head(n = 42)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["people_users"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["people_users"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: people users", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10), 
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))

```


#### Faces & Emotions

```{r}
#| label: gallery-faces-emotions
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "faces_emotions") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["faces_emotions"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["faces_emotions"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: faces emotions", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10), 
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))

```


#### Hands & Arms

```{r}
#| label: gallery-hands-arms
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "hands_arms") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["hands_arms"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["hands_arms"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: hands arms", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))



```

#### Accessibility

```{r}
#| label: gallery-accessibility
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "accessibility") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["accessibility"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["accessibility"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: accessibility", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10), 
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))




```



#### Gender

```{r}
#| label: gallery-gender-identity
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "gender_identity") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["gender_identity"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["gender_identity"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: gender identity", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10), 
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))

```

#### People Social

```{r}
#| label: gallery-people-social
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "people_social") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["people_social"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["people_social"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: people social", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10), 
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```


### UI & Navigation


```{r}
#| label: gallery-ui-navigation
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "ui_navigation") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["ui_navigation"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["ui_navigation"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: ui navigation", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10), 
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```


#### UI Actions

```{r}
#| label: gallery-ui-actions
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "ui_actions") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["ui_actions"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["ui_actions"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: ui actions", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10), 
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))

```


#### UI Controls

```{r}
#| label: gallery-ui-controls-1
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "ui_controls") %>% 
  dplyr::mutate(type = icon)

# First half
df_cat_1 <- df_cat %>% 
  dplyr::slice(1:ceiling(nrow(df_cat)/2))

ggplot(df_cat_1) +
  geom_pop(aes(icon = icon), color = category_colours[["ui_controls"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["ui_controls"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: ui controls (1/2)", subtitle = paste(nrow(df_cat_1), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10), 
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))

```


#### UI Controls (continued)

```{r}
#| label: gallery-ui-controls-2
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "ui_controls") %>% 
  dplyr::mutate(type = icon)

# Second half
df_cat_2 <- df_cat %>% 
  dplyr::slice((ceiling(nrow(df_cat)/2) + 1):nrow(df_cat))

ggplot(df_cat_2) +
  geom_pop(aes(icon = icon), color = category_colours[["ui_controls"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["ui_controls"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: ui controls (2/2)", subtitle = paste(nrow(df_cat_2), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10), 
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))

```


#### Text Formatting

```{r}
#| label: gallery-text-formatting
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "text_formatting") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["text_formatting"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["text_formatting"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: text formatting", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))



```


#### Directional Arrows

```{r}
#| label: gallery-arrows-directional-1
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "arrows_directional") %>% 
  dplyr::mutate(type = icon)

# First half
df_cat_1 <- df_cat %>% 
  dplyr::slice(1:ceiling(nrow(df_cat)/2))

ggplot(df_cat_1) +
  geom_pop(aes(icon = icon), color = category_colours[["arrows_directional"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["arrows_directional"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: arrows directional (1/2)", subtitle = paste(nrow(df_cat_1), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```


#### Directional Arrows (continued)

```{r}
#| label: gallery-arrows-directional-2
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "arrows_directional") %>% 
  dplyr::mutate(type = icon)

# Second half
df_cat_2 <- df_cat %>% 
  dplyr::slice((ceiling(nrow(df_cat)/2) + 1):nrow(df_cat))

ggplot(df_cat_2) +
  geom_pop(aes(icon = icon), color = category_colours[["arrows_directional"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["arrows_directional"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: arrows directional (2/2)", subtitle = paste(nrow(df_cat_2), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))

```


#### Extra Arrows

```{r}
#| label: gallery-arrows-extra
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "arrows_extra") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["arrows_extra"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["arrows_extra"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: arrows extra", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))

```


#### Location & Navigation

```{r}
#| label: gallery-location-navigation
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "location_navigation") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["location_navigation"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
    geom_text(aes(label = type), color = category_colours[["location_navigation"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: location navigation", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))

```


### Files & Data

```{r}
#| label: gallery-files-folders
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "files_folders") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["files_folders"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["files_folders"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: files folders", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title =   element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```

#### Office & Documents

```{r}
#| label: gallery-office-docs
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "office_docs") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["office_docs"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["office_docs"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: office docs", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```

#### Charts & Analytics

```{r}
#| label: gallery-charts-analytics
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "charts_analytics") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["charts_analytics"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["charts_analytics"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: charts analytics", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))

```


### Communication & Technology

```{r}
#| label: gallery-communication
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "communication") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["communication"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["communication"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: communication", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))




```


#### Media Controls

```{r}
#| label: gallery-media-controls
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "media_controls") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["media_controls"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["media_controls"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: media controls", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))




```



#### Devices & Hardware

```{r}
#| label: gallery-devices-hardware
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "devices_hardware") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["devices_hardware"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["devices_hardware"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: devices hardware", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))

```


#### Tech & Science

```{r}
#| label: gallery-tech-science
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "tech_science") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["tech_science"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["tech_science"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: tech science", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```


#### Charts & Analytics

```{r}
#| label: gallery-security-privacy
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "security_privacy")  %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["security_privacy"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["security_privacy"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: security privacy", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))

```


#### Money & Currency

```{r}
#| label: gallery-money-currency
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "money_currency") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["money_currency"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["money_currency"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: money currency", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))
```


#### Media Controls

```{r}
#| label: gallery-shopping-commerce
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "shopping_commerce") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["shopping_commerce"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["shopping_commerce"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: shopping commerce", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))

```

### Medical & Emergency

```{r}
#| label: gallery-medical-health
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "medical_health") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["medical_health"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["medical_health"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: medical health", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))

```


#### Medical Extra

```{r}
#| label: gallery-medical-extra
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "medical_extra") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["medical_extra"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["medical_extra"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: medical extra", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))

```


#### Emergency Hazards

```{r}
#| label: gallery-emergency-hazards
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "emergency_hazards") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["emergency_hazards"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["emergency_hazards"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: emergency hazards", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```


### Transport & Travel

```{r}
#| label: gallery-transport-ground
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "transport_ground") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["transport_ground"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["transport_ground"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: transport ground", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```


#### Air & Sea Transport

```{r}
#| label: gallery-transport-air-sea
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "transport_air_sea") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["transport_air_sea"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["transport_air_sea"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: transport air sea", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```


#### Travel Places

```{r}
#| label: gallery-travel-places
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "travel_places") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["travel_places"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["travel_places"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: travel places", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```


#### Transport Extra

```{r}
#| label: gallery-transport-extra
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "transport_extra") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["transport_extra"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["transport_extra"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: transport extra", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```



### Buildings & Places

```{r}
#| label: gallery-buildings-places-1
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "buildings_places") %>% 
  dplyr::mutate(type = icon)

# First half
df_cat_1 <- df_cat %>% 
  dplyr::slice(1:ceiling(nrow(df_cat)/2))

ggplot(df_cat_1) +
  geom_pop(aes(icon = icon), color = category_colours[["buildings_places"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["buildings_places"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: buildings places (1/2)", subtitle = paste(nrow(df_cat_1), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))

```

#### Buildings & Places (continued)

```{r}
#| label: gallery-buildings-places-2
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "buildings_places") %>% 
  dplyr::mutate(type = icon)

# Second half
df_cat_2 <- df_cat %>% 
  dplyr::slice((ceiling(nrow(df_cat)/2) + 1):nrow(df_cat))

ggplot(df_cat_2) +
  geom_pop(aes(icon = icon), color = category_colours[["buildings_places"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["buildings_places"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: buildings places (2/2)", subtitle = paste(nrow(df_cat_2), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))
```

#### Government & Law

```{r}
#| label: gallery-government-law
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "government_law") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["government_law"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["government_law"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: government law", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```

#### Buildings Extra

```{r}
#| label: gallery-buildings-extra
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "buildings_extra") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["buildings_extra"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["buildings_extra"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: buildings extra", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```

### Religion

```{r}
#| label: gallery-religion-symbols
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "religion_symbols") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["religion_symbols"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["religion_symbols"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: religion symbols", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```


#### Religion Extra

```{r}
#| label: gallery-religion-extra
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "religion_extra") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["religion_extra"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["religion_extra"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: religion extra", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```

### Food, Home & Household

```{r}
#| label: gallery-food-drink
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "food_drink") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["food_drink"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["food_drink"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: food drink", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```


#### Household

```{r}
#| label: gallery-household
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "household") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["household"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["household"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: household", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```

#### Food Extra

```{r}
#| label: gallery-food-extra
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "food_extra") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["food_extra"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["food_extra"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: food extra", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```

### Nature & Environment

```{r}
#| label: gallery-nature
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "nature") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["nature"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["nature"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: nature", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),  
        plot.title = element_text(color="white"),          
        plot.subtitle = element_text(color="white"))


```


#### Weather

```{r}
#| label: gallery-weather
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "weather") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["weather"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["weather"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: weather", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))


```


#### Nature Extra

```{r}
#| label: gallery-nature-extra
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "nature_extra") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["nature_extra"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["nature_extra"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: nature extra", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))


```

### Animals

```{r}
#| label: gallery-animals
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "animals") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["animals"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["animals"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: animals", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))


```

### Sports, Games & Hobbies

```{r}
#| label: gallery-sports
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "sports") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["sports"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["sports"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: sports", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))


```



#### Games & Hobbies

```{r}
#| label: gallery-games-hobbies
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "games_hobbies") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["games_hobbies"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["games_hobbies"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: games hobbies", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))


```

### Tools & Industry


```{r}
#| label: gallery-tools-construction
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "tools_construction") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["tools_construction"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["tools_construction"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: tools construction", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))

```




#### Energy & Industry

```{r}
#| label: gallery-industry-energy
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "industry_energy") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["industry_energy"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["industry_energy"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: industry energy", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))


```


### Time & Symbols

```{r}
#| label: gallery-time
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "time") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["time"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["time"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: time", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))


```

#### Shapes

```{r}
#| label: gallery-shapes-symbols-1
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "shapes_symbols") %>% 
  dplyr::mutate(type = icon)

# First half
df_cat_1 <- df_cat %>% 
  dplyr::slice(1:ceiling(nrow(df_cat)/2))

ggplot(df_cat_1) +
  geom_pop(aes(icon = icon), color = category_colours[["shapes_symbols"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["shapes_symbols"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: shapes symbols (1/2)", subtitle = paste(nrow(df_cat_1), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))

```

#### Shapes (continued)

```{r}
#| label: gallery-shapes-symbols-2
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "shapes_symbols") %>% 
  dplyr::mutate(type = icon)

# Second half
df_cat_2 <- df_cat %>% 
  dplyr::slice((ceiling(nrow(df_cat)/2) + 1):nrow(df_cat))

ggplot(df_cat_2) +
  geom_pop(aes(icon = icon), color = category_colours[["shapes_symbols"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["shapes_symbols"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: shapes symbols (2/2)", subtitle = paste(nrow(df_cat_2), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))
```

### Clothing

```{r}
#| label: gallery-clothing
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "clothing") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["clothing"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["clothing"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: clothing", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))


```


### Entertainment

```{r}
#| label: gallery-entertainment
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "entertainment") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["entertainment"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["entertainment"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: entertainment", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))


```

### Packaging & Objects

```{r}
#| label: gallery-packaging
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "packaging") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["packaging"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["packaging"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: packaging", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))


```

#### Objects Miscellaneous

```{r}
#| label: gallery-objects-misc
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "objects_misc") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["objects_misc"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["objects_misc"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: objects misc", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))


```


### Alphanumeric

```{r}
#| label: gallery-alphanumeric
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "alphanumeric") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["alphanumeric"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["alphanumeric"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: alphanumeric", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))


```


### Brands

```{r}
#| label: gallery-brands-social
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "brands_social") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["brands_social"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["brands_social"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: brands social", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))


```


#### Brands - Development & Cloud

```{r}
#| label: gallery-brands-dev-cloud
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "brands_dev_cloud") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["brands_dev_cloud"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["brands_dev_cloud"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: brands dev cloud", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))


```

#### Brands Commerce

```{r}
#| label: gallery-brands-commerce
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "brands_commerce") %>% 
  dplyr::mutate(type = icon)

ggplot(df_cat) +
  geom_pop(aes(icon = icon), color = category_colours[["brands_commerce"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["brands_commerce"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: brands commerce", subtitle = paste(nrow(df_cat), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))


```



#### Brands - Miscellaneous

```{r}
#| label: gallery-brands-misc-1
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat <- dplyr::filter(df_all, primary_class == "brands_misc") %>% 
  dplyr::mutate(type = icon)

# First eighth
df_cat_1 <- df_cat %>% 
  dplyr::slice(1:ceiling(nrow(df_cat)/8))

ggplot(df_cat_1) +
  geom_pop(aes(icon = icon), color = category_colours[["brands_misc"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["brands_misc"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: brands misc (1/8)", subtitle = paste(nrow(df_cat_1), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))

```




```{r}
#| label: gallery-brands-misc-2
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat_2 <- df_cat %>% 
  dplyr::slice((ceiling(nrow(df_cat)/8) + 1):(2 * ceiling(nrow(df_cat)/8)))

ggplot(df_cat_2) +
  geom_pop(aes(icon = icon), color = category_colours[["brands_misc"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["brands_misc"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: brands misc (2/8)", subtitle = paste(nrow(df_cat_2), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))
```


```{r}
#| label: gallery-brands-misc-3
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat_3 <- df_cat %>% 
  dplyr::slice((2 * ceiling(nrow(df_cat)/8) + 1):(3 * ceiling(nrow(df_cat)/8)))

ggplot(df_cat_3) +
  geom_pop(aes(icon = icon), color = category_colours[["brands_misc"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["brands_misc"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: brands misc (3/8)", subtitle = paste(nrow(df_cat_3), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))
```




```{r}
#| label: gallery-brands-misc-4
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat_4 <- df_cat %>% 
  dplyr::slice((3 * ceiling(nrow(df_cat)/8) + 1):(4 * ceiling(nrow(df_cat)/8)))

ggplot(df_cat_4) +
  geom_pop(aes(icon = icon), color = category_colours[["brands_misc"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["brands_misc"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: brands misc (4/8)", subtitle = paste(nrow(df_cat_4), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))
```


```{r}
#| label: gallery-brands-misc-5
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat_5 <- df_cat %>% 
  dplyr::slice((4 * ceiling(nrow(df_cat)/8) + 1):(5 * ceiling(nrow(df_cat)/8)))

ggplot(df_cat_5) +
  geom_pop(aes(icon = icon), color = category_colours[["brands_misc"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["brands_misc"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: brands misc (5/8)", subtitle = paste(nrow(df_cat_5), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))
```



```{r}
#| label: gallery-brands-misc-6
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat_6 <- df_cat %>% 
  dplyr::slice((5 * ceiling(nrow(df_cat)/8) + 1):(6 * ceiling(nrow(df_cat)/8)))

ggplot(df_cat_6) +
  geom_pop(aes(icon = icon), color = category_colours[["brands_misc"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["brands_misc"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: brands misc (6/8)", subtitle = paste(nrow(df_cat_6), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))
```



```{r}
#| label: gallery-brands-misc-7
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat_7 <- df_cat %>% 
  dplyr::slice((6 * ceiling(nrow(df_cat)/8) + 1):(7 * ceiling(nrow(df_cat)/8)))

ggplot(df_cat_7) +
  geom_pop(aes(icon = icon), color = category_colours[["brands_misc"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["brands_misc"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: brands misc (7/8)", subtitle = paste(nrow(df_cat_7), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))
```



```{r}
#| label: gallery-brands-misc-8
#| echo: FALSE
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
df_cat_8 <- df_cat %>% 
  dplyr::slice((7 * ceiling(nrow(df_cat)/8) + 1):nrow(df_cat))

ggplot(df_cat_8) +
  geom_pop(aes(icon = icon), color = category_colours[["brands_misc"]], size = 2.5, dpi = 100, legend_icons = FALSE) +
  geom_text(aes(label = type), color = category_colours[["brands_misc"]], nudge_y = 0.1, size = 4) +
  scale_y_continuous(NULL, breaks = NULL) +
  scale_x_continuous(NULL, breaks = NULL) +
  labs(title = "primary_class: brands misc (8/8)", subtitle = paste(nrow(df_cat_8), "icons")) +
  theme_pop() +
  theme(legend.position = "none", plot.margin = margin(10, 10, 25, 10),
        plot.title = element_text(color="white"), 
        plot.subtitle = element_text(color="white"))
```