---
title: "fa_icons()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fa_icons()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  message  = FALSE,
  warning  = FALSE
)
library(ggpop)
```

`fa_icons()` searches the bundled Font Awesome icon list by keyword. Use it to
find valid icon names before building your `icon` column.

## Search by keyword

```{r search, eval = FALSE}
fa_icons(query = "person")
fa_icons(query = "car")
fa_icons(query = "heart")
```

```{r search-show}
head(fa_icons(query = "person"), 8)
```

## Common icon categories

Some frequently used categories and example names:

| Category | Example names |
|:---|:---|
| People | `person`, `person-dress`, `user`, `child` |
| Health | `heart`, `stethoscope`, `syringe`, `pill` |
| Transport | `car`, `bicycle`, `plane`, `bus` |
| Nature | `tree`, `leaf`, `seedling`, `sun` |
| UI / shapes | `circle`, `square`, `star`, `check` |

Use `fa_icons(query = "...")` to explore any category. The `name` column in the
result is what goes in your `icon` column or the `icon` parameter.
