---
title: "geom_icon_point()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{geom_icon_point()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  comment    = "#>",
  dpi = 150,
  fig.asp = .9,
  fig.width = 6,
  fig.height = 5,
  out.width = "70%",
  fig.align  = "center",
  message    = FALSE,
  warning    = FALSE
)
library(ggpop)
library(ggplot2)
library(dplyr)
```

`geom_icon_point()` is a drop-in replacement for `geom_point()` that renders
Font Awesome icons instead of dots. No preprocessing needed -- use it directly
with any data frame that has `x` and `y` columns.

## Fixed icon

Use the `icon` parameter (not `aes()`) to display one icon across all points.

```{r fixed}
ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_icon_point(icon = "seedling", size = 1, dpi = 72) +
  scale_color_manual(values = c(
    setosa     = "#43A047",
    versicolor = "#1E88E5",
    virginica  = "#E53935"
  )) +
  labs(title = "Fixed icon", x = "Sepal Length", y = "Petal Length")
```

## Icon per category

Map `icon` inside `aes()` to assign a different icon to each group.

```{r mapped}
df_iris <- iris %>%
  mutate(icon = case_when(
    Species == "setosa"     ~ "seedling",
    Species == "versicolor" ~ "leaf",
    Species == "virginica"  ~ "tree"
  ))

ggplot(df_iris, aes(x = Sepal.Length, y = Petal.Length,
                    color = Species, icon = icon)) +
  geom_icon_point(size = 1, dpi = 72) +
  scale_color_manual(values = c(
    setosa     = "#43A047",
    versicolor = "#1E88E5",
    virginica  = "#E53935"
  )) +
  labs(title = "Icon per species", x = "Sepal Length", y = "Petal Length")
```

## Key parameters

| Parameter | Default | Description |
|:---|:---|:---|
| `icon` | `"person"` | Fixed icon name (overridden by `aes(icon)`) |
| `size` | `2` | Icon size |
| `dpi` | `100` | Render resolution |
| `show.legend` | `NA` | Whether to show legend entry |
