---
title: "Getting Started with ggpop"
format:
  html:
    code-fold: false
    code-summary: "Show the code"
vignette: >
  %\VignetteIndexEntry{Getting Started with ggpop}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

## What is ggpop?

`ggpop` is a `ggplot2` extension for creating **icon-based population charts**. Instead of bars or dots, each observation is represented by a Font Awesome icon — making your data immediately human and intuitive.

This vignette walks you through the core workflow using `geom_pop()`, the main function for building proportional population grids.

---

## Installation

```{r}
#| label: install
#| eval: false
# From CRAN
install.packages("ggpop")

# Development version from GitHub
remotes::install_github("jurjoroa/ggpop")
```

---

## The `geom_pop()` Workflow

`geom_pop()` follows a simple three-step workflow:

1. **Prepare your data** — either use `process_data()` or bring your own data frame (one row per icon, max 1,000)
2. **Assign icons** — map a Font Awesome icon name to each group
3. **Plot** — pass the data to `ggplot()` and add `geom_pop()`

---

## Step 1: Your Data

We start with a simple data frame containing population counts by sex. This mirrors the kind of data you'd typically bring to `geom_pop()`.

```{r}
#| label: data
#| message: false
library(ggpop)
library(ggplot2)
library(dplyr)

df_pop_mx <- data.frame(
  sex     = c("male", "female"),
  n       = c(63459580, 67401427),
  country = "Mexico"
)

df_pop_mx
```

---

## Step 2: Process the Data

`process_data()` converts raw population counts into a sampled data frame where each row represents one icon. It calculates group proportions and allocates icons accordingly.

```{r}
#| label: process
df_processed <- process_data(
  data        = df_pop_mx,
  group_var   = sex,
  sum_var     = n,
  sample_size = 100
)

head(df_processed)
```

> **Note:** `process_data()` is optional. If your data already has one row per icon (up to 1,000 rows), you can pass it directly to `geom_pop()`.

---

## Step 3: Assign Icons

Add an `icon` column to your processed data. Icon names come from Font Awesome — use any of the 2,000+ free icons.


```{r}
#| label: icons-querry
#| eval: false

fa_icons(query = "person")

```

```{r}
#| label: icons-querry-1
#| echo: false
#| message: false
#| warning: false

library(reactable)
library(reactablefmtr)

fa_icons(query = "person") %>% 
  reactable(
    searchable = TRUE,
    filterable = TRUE,
    defaultPageSize = 10
  )

```



We selected the `male` and `female` icons for our population chart. You can choose any icons that fit your data and story!

```{r}
#| label: icons-choose

df_processed <- df_processed %>%
  mutate(icon = case_when(
    type == "male"   ~ "male",
    type == "female" ~ "female"
  ))
```

---

## Step 4: Plot

Pass the data to `ggplot()` and add `geom_pop()`. Map `icon` and `color` to your grouping variable.

```{r}
#| label: basic-plot
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")

ggplot() +
  geom_pop(
    data = df_processed,
    aes(icon = icon, color = type),
    size = 2,
    dpi  = 100
  ) +
  scale_color_manual(values = c("male" = "#1E88E5", "female" = "#D81B60")) +
  theme_pop(base_size=15) +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  labs(
    title    = "Mexico Population by Sex (2024)",
    subtitle = "Each icon represents ~1% of the total population",
    color    = "Sex"
  )
```

---

## Scaling legend icons

Use `scale_legend_icon()` to control the legend icon size. You can also turn off legend icons with `legend_icons = FALSE` in `geom_pop()` if you prefer a text-only legend with dots

```{r}
#| label: legend-plot
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
ggplot(data = df_processed, aes(icon = icon, color = type)) +
  geom_pop(size = 2, dpi = 100, legend_icons = TRUE) +
  scale_color_manual(values = c("male" = "#1E88E5", "female" = "#D81B60")) +
  theme_pop(base_size=15) +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  scale_legend_icon(size = 10) +
  labs(title    = "Mexico Population by Sex (2024)",
       subtitle = "Each icon represents ~1% of the total population",
       color    = "Sex")
```

---

## Using Your Own Data

You don't need `process_data()`. As long as the dataframe doesn't have more than 1,000 rows, it works. You can also do a facet or use `cowplot` so you can have more panes. Any data frame with one row per icon works directly:

```{r}
#| label: own-data-querry
#| eval: false
fa_icons(query = "bed")

```

```{r}
#| label: own-data-querry-1
#| echo: false
#| message: false
#| warning: false

library(reactable)
library(reactablefmtr)

fa_icons(query = "bed") %>% 
  reactable(
    searchable = TRUE,
    filterable = TRUE,
    defaultPageSize = 10
  )

```


We created a simple data frame with 100 rows, representing a population of patients with three health statuses: "Healthy", "At Risk", and "Ill". Each status is mapped to a different icon.


```{r}
#| label: own-data
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")


# Our own data frame with one row per icon
df_simple <- data.frame(
  group = c(rep("Healthy", 70), rep("At Risk", 20), rep("Ill", 10)),
  icon  = c(rep("person", 70), rep("person-half-dress", 20), rep("bed-pulse", 10))
)

# Set factor levels to control legend order
df_simple$group <- factor(df_simple$group, levels = c("Healthy", "At Risk", "Ill"))

ggplot(data = df_simple, aes(icon = icon, color = group)) +
  geom_pop(size = 2, dpi = 100, legend_icons = TRUE) +
  scale_color_manual(values = c(
    "Healthy"  = "#43A047",
    "At Risk"  = "#FFB300",
    "Ill"      = "#E53935"
  )) +
  theme_pop(base_size = 15) +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  scale_legend_icon(size = 8) +
  labs( title    = "Simulated Patient Population (n = 100)",
        subtitle = "Each icon represents one patient",
        color    = "Status")

```

---

## Next Steps

- **`geom_icon_point()`** — use icons as scatter plot points on any x/y data
- **Faceting** — split your population chart by group using `facet_wrap()` or `geofacet`
- **Themes** — explore `theme_pop()` and customize with standard ggplot2 theme options
