---
title: "Getting Started with ggpop"
format:
  html:
    code-fold: false
    code-summary: "Show the code"
vignette: >
  %\VignetteIndexEntry{Getting Started with ggpop}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

## What is ggpop?
<div style="line-height: 0.6;"><br></div>

`ggpop` is a `ggplot2` extension for creating **icon-based population charts**. Instead of bars or dots, each observation is represented by a Font Awesome icon — making your data immediately human and intuitive.

This vignette walks you through the core workflow using `geom_pop()`, the main function for building proportional population grids.

<div style="line-height: 0.6;"><br></div>

---

## Installation
<div style="line-height: 0.6;"><br></div>

```{r}
#| label: install
#| eval: false
# From CRAN
install.packages("ggpop")

# Development version from GitHub
remotes::install_github("jurjoroa/ggpop")
```

<div style="line-height: 0.6;"><br></div>

---

## The `geom_pop()` Workflow
<div style="line-height: 0.6;"><br></div>

`geom_pop()` follows a simple three-step workflow:

1. **Prepare your data** — either use `process_data()` or bring your own data frame (one row per icon, max 1,000)
2. **Assign icons** — map a Font Awesome icon name to each group
3. **Plot** — pass the data to `ggplot()` and add `geom_pop()`

<div style="line-height: 0.6;"><br></div>

---

## Step 1: Your Data
<div style="line-height: 0.6;"><br></div>

We start with a simple data frame containing population counts by sex. This mirrors the kind of data you'd typically bring to `geom_pop()`.

```{r}
#| label: data
#| message: false
library(ggpop)
library(ggplot2)
library(dplyr)

df_pop_mx <- data.frame(
  sex     = c("male", "female"),
  n       = c(63459580, 67401427),
  country = "Mexico"
)

df_pop_mx
```

<div style="line-height: 0.6;"><br></div>

---

## Step 2: Process the Data
<div style="line-height: 0.6;"><br></div>

`process_data()` converts raw population counts into a sampled data frame where each row represents one icon. It calculates group proportions and allocates icons accordingly.

```{r}
#| label: process
df_processed <- process_data(
  data        = df_pop_mx,
  group_var   = sex,
  sum_var     = n,
  sample_size = 100
)

head(df_processed)
```

> **Note:** `process_data()` is optional. If your data already has one row per icon (up to 1,000 rows), you can pass it directly to `geom_pop()`.

<div style="line-height: 0.6;"><br></div>

---

## Step 3: Assign Icons
<div style="line-height: 0.6;"><br></div>

Add an `icon` column to your processed data. Icon names come from Font Awesome — use any of the 2,000+ free icons.


```{r}
#| label: icons-querry
#| eval: false

fa_icons(query = "person")

```

```{r}
#| label: icons-querry-1
#| echo: false
#| message: false
#| warning: false

library(reactable)
library(reactablefmtr)

fa_icons(query = "person") %>% 
  reactable(
    searchable = TRUE,
    filterable = TRUE,
    defaultPageSize = 10
  )

```



We selected the `male` and `female` icons for our population chart. You can choose any icons that fit your data and story!

```{r}
#| label: icons-choose

df_processed <- df_processed %>%
  mutate(icon = case_when(
    type == "male"   ~ "male",
    type == "female" ~ "female"
  ))
```

<div style="line-height: 0.6;"><br></div>

---

## Step 4: Plot
<div style="line-height: 0.6;"><br></div>

Pass the data to `ggplot()` and add `geom_pop()`. Map `icon` and `color` to your grouping variable.

```{r}
#| label: basic-plot
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")

ggplot() +
  geom_pop(
    data = df_processed,
    aes(icon = icon, color = type),
    size = 2,
    dpi  = 100
  ) +
  scale_color_manual(values = c("male" = "#1E88E5", "female" = "#D81B60")) +
  theme_pop(base_size=15) +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  labs(
    title    = "Mexico Population by Sex (2024)",
    subtitle = "Each icon represents ~1% of the total population",
    color    = "Sex"
  )
```

<div style="line-height: 0.6;"><br></div>

---

## Scaling legend icons
<div style="line-height: 0.6;"><br></div>

Use `scale_legend_icon()` to control the legend icon size. You can also turn off legend icons with `legend_icons = FALSE` in `geom_pop()` if you prefer a text-only legend with dots

```{r}
#| label: legend-plot
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")
ggplot(data = df_processed, aes(icon = icon, color = type)) +
  geom_pop(size = 2, dpi = 100, legend_icons = TRUE) +
  scale_color_manual(values = c("male" = "#1E88E5", "female" = "#D81B60")) +
  theme_pop(base_size=15) +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  scale_legend_icon(size = 10) +
  labs(title    = "Mexico Population by Sex (2024)",
       subtitle = "Each icon represents ~1% of the total population",
       color    = "Sex")
```

<div style="line-height: 0.6;"><br></div>

---

## Using Your Own Data
<div style="line-height: 0.6;"><br></div>

You don't need `process_data()`. As long as the dataframe doesn't have more than 1,000 rows, it works. You can also do a facet or use `cowplot` so you can have more panes. Any data frame with one row per icon works directly:

```{r}
#| label: own-data-querry
#| eval: false
fa_icons(query = "bed")

```

```{r}
#| label: own-data-querry-1
#| echo: false
#| message: false
#| warning: false

library(reactable)
library(reactablefmtr)

fa_icons(query = "bed") %>% 
  reactable(
    searchable = TRUE,
    filterable = TRUE,
    defaultPageSize = 10
  )

```


We created a simple data frame with 100 rows, representing a population of patients with three health statuses: "Healthy", "At Risk", and "Ill". Each status is mapped to a different icon.


```{r}
#| label: own-data
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")


# Our own data frame with one row per icon
df_simple <- data.frame(
  group = c(rep("Healthy", 70), rep("At Risk", 20), rep("Ill", 10)),
  icon  = c(rep("person", 70), rep("person-half-dress", 20), rep("bed-pulse", 10))
)

# Set factor levels to control legend order
df_simple$group <- factor(df_simple$group, levels = c("Healthy", "At Risk", "Ill"))

ggplot(data = df_simple, aes(icon = icon, color = group)) +
  geom_pop(size = 2, dpi = 100, legend_icons = TRUE) +
  scale_color_manual(values = c(
    "Healthy"  = "#43A047",
    "At Risk"  = "#FFB300",
    "Ill"      = "#E53935"
  )) +
  theme_pop(base_size = 15) +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  scale_legend_icon(size = 8) +
  labs( title    = "Simulated Patient Population (n = 100)",
        subtitle = "Each icon represents one patient",
        color    = "Status")

```

<div style="line-height: 0.6;"><br></div>

---


## Use geom_text() as a label
<div style="line-height: 0.6;"><br></div>

`geom_pop()` exposes its internally computed icon coordinates to downstream layers. This means you can add `geom_text()` — or any ggplot2 geom — **without specifying `x` or `y`**: they are inherited automatically from the icon grid.

This is useful when you want labels to float over the icons instead of relying on a legend. Set `show.legend = FALSE` in `geom_pop()`.

```{r}
#| label: geom-text-label
#| message: false
#| warning: false
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")

df_labeled <- data.frame(
  name = c(
    # Female names (50)
    "María", "Guadalupe", "Juana", "Margarita", "Francisca",
    "Teresa", "Rosa", "Antonia", "Ana", "Isabel",
    "Carmen", "Josefina", "Laura", "Verónica", "Patricia",
    "Leticia", "Silvia", "Elizabeth", "Adriana", "Martha",
    "Elena", "Gabriela", "Alejandra", "Gloria", "Claudia",
    "Lucía", "Beatriz", "Daniela", "Mónica", "Rocío",
    "Alma", "Karla", "Yolanda", "Diana", "Sandra",
    "Cecilia", "Paola", "Norma", "Angélica", "Irma",
    "Liliana", "Brenda", "Jessica", "Susana", "Blanca",
    "Marisol", "Carolina", "Luz", "Cristina", "Andrea",
    # Male names (50)
    "José", "Juan", "Luis", "Miguel", "Carlos",
    "Francisco", "Antonio", "Jesús", "Pedro", "Manuel",
    "Alejandro", "Jorge", "Rafael", "Roberto", "Fernando",
    "Daniel", "Ricardo", "Javier", "Alberto", "Sergio",
    "Raúl", "Enrique", "Guillermo", "Oscar", "Gerardo",
    "Arturo", "Héctor", "Eduardo", "Armando", "David",
    "Víctor", "Pablo", "Ángel", "Ramón", "Andrés",
    "Mario", "Salvador", "Ignacio", "Gustavo", "Alfredo",
    "Rubén", "Marco", "Rodrigo", "Joaquín", "Martín",
    "Gabriel", "Felipe", "Ernesto", "Leonardo", "Sebastián"
  ),
  gender = c(rep("Female", 50), rep("Male", 50)),
  icon = c(rep("person-dress", 50), rep("person", 50))
)

df_labeled$gender <- factor(df_labeled$gender,
                            levels = c("Female", "Male"))

ggplot(data = df_labeled, aes(icon = icon, color = gender)) +
  geom_pop(size = 2, dpi = 100, show.legend = FALSE, ncol = 10) +
  geom_text(
    aes(label = name),
    nudge_y       = 0.08,
    size          = 4,
    fontface      = "bold",
    check_overlap = TRUE
  ) +
  scale_color_manual(values = c(
    "Female" = "#E91E63",
    "Male"   = "#2196F3"
  )) +
  theme_pop(base_size = 20) +
  theme(
    plot.title    = element_text(color = "white", hjust = .5),
    plot.subtitle = element_text(color = "white", hjust = .5),
    legend.position = "none"
  ) +
  labs(
    title    = "100 Most Common Names in Mexico",
    subtitle = "Pink icons represent female names, blue icons represent male names"
  )

```

<div style="line-height: 0.6;"><br></div>

---

## Next Steps
<div style="line-height: 0.6;"><br></div>

- **`geom_icon_point()`** — use icons as scatter plot points on any x/y data
- **Faceting** — split your population chart by group using `facet_wrap()` or `geofacet`
- **Themes** — explore `theme_pop()` and customize with standard ggplot2 theme options
