---
title: "Getting Started with ggpop"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with ggpop}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  fig.width  = 7,
  fig.height = 5,
  dpi = 100,
  out.width = "100%"
)
```

## What is ggpop?

`ggpop` is a `ggplot2` extension for creating **icon-based population charts**. Instead of bars or dots, each observation is represented by a Font Awesome icon — making your data immediately human and intuitive.

This vignette walks you through the core workflow using `geom_pop()`, the main function for building proportional population grids.

---

## Installation

```{r install, eval = FALSE}
# From CRAN
install.packages("ggpop")

# Development version from GitHub
remotes::install_github("jurjoroa/ggpop")
```

---

## The `geom_pop()` Workflow

`geom_pop()` follows a simple three-step workflow:

1. **Prepare your data** — either use `process_data()` or bring your own data frame (one row per icon, max 1,000)
2. **Assign icons** — map a Font Awesome icon name to each group
3. **Plot** — pass the data to `ggplot()` and add `geom_pop()`

---

## Step 1: Your Data

We start with a simple data frame containing population counts by sex. This mirrors the kind of data you'd typically bring to `geom_pop()`.

```{r data}
library(ggpop)
library(ggplot2)
library(dplyr)

df_pop_mx <- data.frame(
  sex     = c("male", "female"),
  n       = c(63459580, 67401427),
  country = "Mexico"
)

df_pop_mx
```

---

## Step 2: Process the Data

`process_data()` converts raw population counts into a sampled data frame where each row represents one icon. It calculates group proportions and allocates icons accordingly.

```{r process}
df_processed <- process_data(
  data        = df_pop_mx,
  group_var   = sex,
  sum_var     = n,
  sample_size = 100
)

head(df_processed)
```

> **Note:** `process_data()` is optional. If your data already has one row per icon (up to 1,000 rows), you can pass it directly to `geom_pop()`.

---

## Step 3: Assign Icons

Add an `icon` column to your processed data. Icon names come from Font Awesome — use any of the 2,000+ free icons.

```{r icons}
df_processed <- df_processed %>%
  mutate(icon = case_when(
    type == "male"   ~ "male",
    type == "female" ~ "female"
  ))
```

---

## Step 4: Plot

Pass the data to `ggplot()` and add `geom_pop()`. Map `icon` and `color` to your grouping variable.

```{r basic-plot}
ggplot() +
  geom_pop(
    data = df_processed,
    aes(icon = icon, color = type),
    size = 2,
    dpi  = 100
  ) +
  scale_color_manual(values = c("male" = "#1E88E5", "female" = "#D81B60")) +
  theme_pop() +
  labs(
    title    = "Mexico Population by Sex (2024)",
    subtitle = "Each icon represents ~1% of the total population",
    color    = "Sex"
  )
```

---

## Adding a Legend with Icons

Set `legend_icons = TRUE` inside `geom_pop()` and use `scale_legend_icon()` to control the legend icon size.

```{r legend-plot}
ggplot() +
  geom_pop(
    data         = df_processed,
    aes(icon = icon, color = type),
    size         = 2,
    dpi          = 100,
    legend_icons = TRUE
  ) +
  scale_color_manual(values = c("male" = "#1E88E5", "female" = "#D81B60")) +
  scale_legend_icon(size = 5) +
  theme_pop() +
  labs(
    title    = "Mexico Population by Sex (2024)",
    subtitle = "Each icon represents ~1% of the total population",
    color    = "Sex"
  )
```

---

## Using Your Own Data

You don't need `process_data()`. Any data frame with one row per icon works directly:

```{r own-data}
df_simple <- data.frame(
  group = c(rep("Healthy", 70), rep("At Risk", 20), rep("Ill", 10)),
  icon  = c(rep("person", 70), rep("person-half-dress", 20), rep("bed-pulse", 10))
)

df_simple$group <- factor(df_simple$group, levels = c("Healthy", "At Risk", "Ill"))

ggplot() +
  geom_pop(
    data         = df_simple,
    aes(icon = icon, color = group),
    size         = 2,
    dpi          = 100,
    legend_icons = TRUE
  ) +
  scale_color_manual(values = c(
    "Healthy"  = "#43A047",
    "At Risk"  = "#FFB300",
    "Ill"      = "#E53935"
  )) +
  scale_legend_icon(size = 5) +
  theme_pop() +
  labs(
    title    = "Simulated Patient Population (n = 100)",
    subtitle = "Each icon represents one patient",
    color    = "Status"
  )
```

---

## Next Steps

- **`geom_icon_point()`** — use icons as scatter plot points on any x/y data
- **Faceting** — split your population chart by group using `facet_wrap()` or `geofacet`
- **Themes** — explore `theme_pop()` and customize with standard ggplot2 theme options

Visit the [ggpop website](https://jurjoroa.github.io/ggpop/) for the full function reference and more examples.
