---
title: "Preparing Data with process_data()"
format:
  html:
    code-fold: false
    code-summary: "Show the code"
vignette: >
  %\VignetteIndexEntry{Preparing Data with process_data()}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

## What is `process_data()`?

`process_data()` is a helper function that converts raw population counts into a sampled data frame ready for `geom_pop()`. Each row in the output represents one icon in the final chart.

It handles:

- Calculating group proportions from raw counts
- Proportionally allocating a fixed sample size across groups
- Supporting hierarchical grouping via `high_group_var`

```{r}
#| label: load
#| message: false
library(ggpop)
library(ggplot2)
library(dplyr)
```

---

## Basic Usage

The minimum inputs are `data`, `group_var` (the grouping column), and `sum_var` (the count column). `sample_size` controls how many icons appear in the final chart (max 1,000).

```{r}
#| label: basic
df_sex <- data.frame(
  sex = c("male", "female"),
  n   = c(63459580, 67401427)
)

df_sex_proc <- process_data(
  data        = df_sex,
  group_var   = sex,
  sum_var     = n,
  sample_size = 100
)

head(df_sex_proc)
```

The output contains:

- **type**: group label (from `group_var`)
- **n**: total count for that group
- **prop**: proportion of the total
- One row per sampled icon

---

## Understanding Proportions

`process_data()` calculates each group's share of the total and allocates icons proportionally. With `sample_size = 100`, a group with 48% of the population gets ~48 icons.

```{r}
#| label: proportions
df_sex_proc %>%
  group_by(type) %>%
  summarise(
    icons      = n(),
    proportion = round(mean(prop) * 100, 1)
  )
```

---

## Multiple Groups

Works with any number of groups — not just two.

```{r}
#| label: multi-group
df_regions <- data.frame(
  region = c("North", "South", "East", "West"),
  n      = c(12000, 8000, 15000, 5000)
)

df_regions_processed <- process_data(
  data        = df_regions,
  group_var   = region,
  sum_var     = n,
  sample_size = 100
)

df_regions_processed %>%
  group_by(type) %>%
  summarise(icons = n())
```

---

## Hierarchical Grouping with `high_group_var`

Use `high_group_var` to nest groups under a higher-level category. This is useful when you want to facet by a parent group while preserving sub-group icon assignments.

```{r}
#| label: hierarchical
df_health <- data.frame(
  region    = c("North", "South", "East", "West",
                "North", "South", "East", "West"),
  status    = c(rep("Healthy", 4), rep("At Risk", 4)),
  n         = c(8000, 6000, 9000, 4000,
                4000, 2000, 6000, 1000)
)

df_health_processed <- process_data(
  data           = df_health,
  group_var      = status,
  sum_var        = n,
  high_group_var = "region",
  sample_size    = 100
)

df_health_processed %>%
  group_by(group, type) %>%
  summarise(icons = n(), .groups = "drop")
```

---

## Skipping `process_data()`

`process_data()` is optional. If your data already has one row per icon, pass it directly to `geom_pop()`. The only requirement is a maximum of 1,000 rows per plot (or per facet group).

```{r}
#| label: skip
#| fig-width: 10
#| fig-height: 10
#| dev: png
#| dev-args: !expr list(bg = "transparent")

df_direct <- data.frame(
  activity = c(
    rep("Walking",  35),
    rep("Running",  25),
    rep("Hiking",   20),
    rep("Cycling",  15),
    rep("Swimming",  5)
  ),
  icon = c(
    rep("person-walking",  35),
    rep("person-running",  25),
    rep("person-hiking",   20),
    rep("person-biking",   15),
    rep("person-swimming",  5)
  )
)

# Pass directly — no process_data() needed
ggplot() +
  geom_pop(
    data = df_direct,
    aes(icon = icon, color = activity),
    size = 2, dpi = 100, legend_icons = TRUE, arrange = TRUE
  ) +
  scale_color_manual(values = c(
    "Walking"  = "#5C6BC0",
    "Running"  = "#E53935",
    "Hiking"   = "#43A047",
    "Cycling"  = "#FFB300",
    "Swimming" = "#039BE5"
  )) +
  theme_pop() +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  scale_legend_icon(size = 8) +
  labs(
    title    = "Physical Activity Distribution (n = 100)",
    subtitle = "Each icon represents one survey participant",
    color    = "Activity"
  )
```

---

## Summary

| Parameter | Description |
|:---|:---|
| `data` | Input data frame with group counts |
| `group_var` | Column to group by (unquoted) |
| `sum_var` | Column with population counts |
| `sample_size` | Number of icons to generate (max 1,000) |
| `high_group_var` | Optional parent grouping for faceting |

