---
title: "Themes & Customization"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Themes & Customization}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  fig.width  = 7,
  fig.height = 5,
  dpi = 100,
  out.width = "100%"
)
```

```{r load}
library(ggpop)
library(ggplot2)
library(dplyr)
```

```{r shared-data, include = FALSE}
df <- data.frame(
  sex = c("male", "female"),
  n   = c(63459580, 67401427)
)

df_processed <- process_data(
  data        = df,
  group_var   = sex,
  sum_var     = n,
  sample_size = 100
) %>%
  mutate(icon = case_when(
    type == "male"   ~ "male",
    type == "female" ~ "female"
  ))
```

## Themes Overview

`ggpop` ships with three built-in themes, all optimized for icon-based charts:

| Theme | Description |
|:---|:---|
| `theme_pop()` | Default — clean, minimal, no axes |
| `theme_pop_dark()` | Dark background variant |
| `theme_pop_minimal()` | Ultra-minimal, no legend or titles |

---

## `theme_pop()`

The default theme. Removes axes and gridlines, keeping the focus on the icons. All standard ggplot2 `theme()` arguments can be added on top.

```{r theme-pop}
ggplot() +
  geom_pop(
    data         = df_processed,
    aes(icon = icon, color = type),
    size         = 2,
    dpi          = 100,
    legend_icons = TRUE
  ) +
  scale_color_manual(values = c("male" = "#1E88E5", "female" = "#D81B60")) +
  scale_legend_icon(size = 5) +
  theme_pop() +
  labs(
    title    = "Mexico Population by Sex (2024)",
    subtitle = "Each icon represents ~1% of the total population",
    color    = "Sex"
  )
```

### Parameters

- **`base_size`**: controls font size throughout (default: `11`)
- **`legend_position`**: `"right"`, `"bottom"`, `"left"`, `"top"`, or `"none"`
- **`plot_margin`**: single number or `margin()` object

```{r theme-pop-params}
ggplot() +
  geom_pop(
    data         = df_processed,
    aes(icon = icon, color = type),
    size         = 2,
    dpi          = 100,
    legend_icons = TRUE
  ) +
  scale_color_manual(values = c("male" = "#1E88E5", "female" = "#D81B60")) +
  scale_legend_icon(size = 5) +
  theme_pop(base_size = 14, legend_position = "bottom") +
  labs(
    title = "Larger text, legend at bottom",
    color = "Sex"
  )
```

---

## `theme_pop_dark()`

A dark variant built on top of `theme_pop()`. Accepts `bg_color` and `text_color` for full control.

```{r theme-pop-dark}
ggplot() +
  geom_pop(
    data         = df_processed,
    aes(icon = icon, color = type),
    size         = 2,
    dpi          = 100,
    legend_icons = TRUE
  ) +
  scale_color_manual(values = c("male" = "#64B5F6", "female" = "#F48FB1")) +
  scale_legend_icon(size = 5) +
  theme_pop_dark() +
  labs(
    title    = "Mexico Population by Sex (2024)",
    subtitle = "Dark theme — ideal for presentations",
    color    = "Sex"
  )
```

Custom background and text colors:

```{r theme-pop-dark-custom}
ggplot() +
  geom_pop(
    data         = df_processed,
    aes(icon = icon, color = type),
    size         = 2,
    dpi          = 100,
    legend_icons = TRUE
  ) +
  scale_color_manual(values = c("male" = "#80DEEA", "female" = "#FF8A65")) +
  scale_legend_icon(size = 5) +
  theme_pop_dark(bg_color = "#0D1B2A", text_color = "#E0F2F1") +
  labs(
    title    = "Mexico Population by Sex (2024)",
    subtitle = "Custom dark background",
    color    = "Sex"
  )
```

---

## `theme_pop_minimal()`

Strips everything — no title, no legend, no margins. Best for embedding icon arrays inside dashboards or documents.

```{r theme-pop-minimal}
ggplot() +
  geom_pop(
    data = df_processed,
    aes(icon = icon, color = type),
    size = 2,
    dpi  = 100
  ) +
  scale_color_manual(values = c("male" = "#1E88E5", "female" = "#D81B60")) +
  theme_pop_minimal()
```

---

## `scale_legend_icon()`

Controls the size of icons in the legend. Use it alongside `legend_icons = TRUE` in `geom_pop()` or `geom_icon_point()`.

```{r scale-legend}
ggplot() +
  geom_pop(
    data         = df_processed,
    aes(icon = icon, color = type),
    size         = 2,
    dpi          = 100,
    legend_icons = TRUE
  ) +
  scale_color_manual(values = c("male" = "#1E88E5", "female" = "#D81B60")) +
  scale_legend_icon(size = 8) +
  theme_pop() +
  labs(title = "Larger legend icons with scale_legend_icon(size = 8)", color = "Sex")
```

---

## `stroke_width` — Icon Outlines

Add an outline to icons with `stroke_width`. Higher values produce a thicker border, useful for light icons on light backgrounds.

```{r stroke}
ggplot() +
  geom_pop(
    data         = df_processed,
    aes(icon = icon, color = type),
    size         = 2,
    dpi          = 100,
    legend_icons = TRUE,
    stroke_width = 8
  ) +
  scale_color_manual(values = c("male" = "#1E88E5", "female" = "#D81B60")) +
  scale_legend_icon(size = 5) +
  theme_pop() +
  labs(title = "Icons with stroke_width = 8", color = "Sex")
```

---

## Combining with ggplot2 `theme()`

`theme_pop()` is a standard ggplot2 theme — add any `theme()` call on top to override specific elements.

```{r custom-theme}
ggplot() +
  geom_pop(
    data         = df_processed,
    aes(icon = icon, color = type),
    size         = 2,
    dpi          = 100,
    legend_icons = TRUE
  ) +
  scale_color_manual(values = c("male" = "#1E88E5", "female" = "#D81B60")) +
  scale_legend_icon(size = 5) +
  theme_pop() +
  theme(
    plot.background  = element_rect(fill = "#F5F5F5", color = NA),
    plot.title       = element_text(color = "#1E88E5", face = "bold", size = 16),
    plot.subtitle    = element_text(color = "#546E7A"),
    legend.text      = element_text(color = "#37474F"),
    plot.margin      = margin(20, 20, 20, 20)
  ) +
  labs(
    title    = "Customized with theme()",
    subtitle = "theme_pop() + additional theme() overrides",
    color    = "Sex"
  )
```

---

## Summary

| Function | Purpose |
|:---|:---|
| `theme_pop()` | Default clean theme for icon charts |
| `theme_pop_dark()` | Dark background variant |
| `theme_pop_minimal()` | No legend, no titles, no margins |
| `scale_legend_icon(size)` | Control legend icon size |
| `stroke_width` | Add outline to icons in `geom_pop()` / `geom_icon_point()` |

Visit the [ggpop website](https://jurjoroa.github.io/ggpop/) for the full function reference.
