---
title: "Tips & Best Practices"
format:
  html:
    code-fold: false
    code-summary: "Show the code"
vignette: >
  %\VignetteIndexEntry{Tips & Best Practices}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label: setup
#| include: false
#| message: false
#| warning: false
library(ggpop)
library(ggplot2)
library(dplyr)
```

This page collects the most important rules and conventions to keep in mind when working with `ggpop`. Each tip explains what to do (and why), followed by a working example.

<div style="line-height: 0.6;"><br></div>

---

## Tip 1 — Use valid Font Awesome icon names

The `icon` column (or `aes(icon = ...)`) must contain **valid Font Awesome icon names** — no `NA` values, no whitespace-only strings, and no names that don't exist in Font Awesome. Use `fa_icons()` to look up available names before building your plot.

::: {.callout-tip}
## How to find valid icon names
```r
# Search by keyword
fa_icons(query = "person")
fa_icons(query = "car")
fa_icons(query = "heart")
```
:::

```{r}
#| label: tip1
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
df_tip1 <- data.frame(
  transport = rep(c("Car", "Bicycle", "Plane"), each = 10),
  icon      = rep(c("car", "bicycle", "plane"), each = 10),
  stringsAsFactors = FALSE
)

ggplot() +
  geom_pop(
    data = df_tip1,
    aes(icon = icon, color = transport),
    size = 3, dpi = 100, legend_icons = TRUE
  ) +
  scale_color_manual(values = c(
    "Car"     = "#E64A19",
    "Bicycle" = "#2E7D32",
    "Plane"   = "#1565C0"
  )) +
  theme_pop() +
  scale_legend_icon(size = 8) +
  labs(title = "Tip 1: Valid FA icon names", color = "Transport")
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 2 — Avoid reserved column names

`ggpop` uses several internal column names during layout computation. If your data already contains any of these names, the geom will throw an error:

| Reserved name | Purpose |
|:---|:---|
| `x1` | Computed x position |
| `y1` | Computed y position |
| `pos` | Icon position index |
| `image` | PNG path (internal) |
| `coord_size` | Coordinate scaling |
| `icon_size` | Icon rendering size |
| `icon_stroke_width` | Stroke scaling |
| `alpha` | Icon transparency (internal) |

**Rename any conflicting columns before calling `geom_pop()` or `geom_icon_point()`.**

```{r}
#| label: tip2
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
# Safe column names — no conflict with internal reserved names
df_tip2 <- data.frame(
  sex      = rep(c("Male", "Female"), each = 20),
  icon     = rep(c("mars", "venus"), each = 20),
  age_grp  = rep(c("Adult", "Child"), times = 20),  # safe name
  stringsAsFactors = FALSE
)

ggplot() +
  geom_pop(
    data = df_tip2,
    aes(icon = icon, color = sex),
    size = 3, dpi = 100, legend_icons = TRUE
  ) +
  scale_color_manual(values = c("Male" = "#1565C0", "Female" = "#C62828")) +
  theme_pop() +
  scale_legend_icon(size = 8) +
  labs(title = "Tip 2: Safe column names", color = "Sex")
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 3 — Use `color`, not `fill`

`geom_pop()` renders icons as raster images. This means:

- `fill` is **not supported** → hard error
- **`color`** is the correct aesthetic for icon color
- **`alpha`** is supported — either as a fixed parameter (`geom_pop(alpha = 0.5)`) or mapped via `aes(alpha = col)`, but **`alpha` is a reserved column name** — rename your column first (e.g. `opacity`)

::: {.callout-important}
## What NOT to do
```r
# fill will error in geom_pop():
aes(icon = icon, group = sex, fill = sex)   # Error
```
:::

```{r}
#| label: tip3
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
df_tip3 <- data.frame(
  region = rep(c("North", "South", "East", "West"), each = 15),
  icon   = rep(c("compass", "arrow-down", "arrow-right", "arrow-left"), each = 15),
  stringsAsFactors = FALSE
)

ggplot() +
  geom_pop(
    data = df_tip3,
    aes(icon = icon, color = region,  alpha = 0.5),                       # fixed alpha ✓ — works as a 
    size = 3, dpi = 100, legend_icons = TRUE
  ) +
  scale_color_manual(values = c(
    "North" = "#00897B", "South" = "#E64A19",
    "East"  = "#7B1FA2", "West"  = "#F9A825"
  )) +
  theme_pop() +
  scale_legend_icon(size = 8) +
  labs(title = "Tip 3: Use color, not fill", color = "Region")
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 4 — Keep your total icon count at or below 1,000

`geom_pop()` enforces a hard limit of **1,000 icons** — both globally and per facet panel. Exceeding this limit raises an error immediately. Use `process_data()` with a `sample_size` argument to control the icon count automatically.

```{r}
#| label: tip4
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
df_tip4_raw <- data.frame(
  group = c("Group A", "Group B", "Group C"),
  n     = c(4500000, 3200000, 2100000)
)

# process_data samples down to sample_size icons total
df_tip4 <- process_data(
  data        = df_tip4_raw,
  group_var   = group,
  sum_var     = n,
  sample_size = 100          # stays well under the 1,000 limit
) %>%
  mutate(icon = case_when(
    type == "Group A" ~ "circle",
    type == "Group B" ~ "square",
    type == "Group C" ~ "triangle-exclamation"
  ))

ggplot() +
  geom_pop(
    data = df_tip4,
    aes(icon = icon, color = type),
    size = 2, dpi = 100, legend_icons = TRUE
  ) +
  scale_color_manual(values = c(
    "Group A" = "#1565C0",
    "Group B" = "#2E7D32",
    "Group C" = "#E64A19"
  )) +
  theme_pop() +
  scale_legend_icon(size = 8) +
  labs(
    title    = "Tip 4: Use process_data() to control icon count",
    subtitle = "sample_size = 100 — well under the 1,000-icon limit",
    color    = "Group"
  )
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 5 — Don't map `x` or `y` in `geom_pop()`

`geom_pop()` computes icon positions internally in a grid layout. Mapping `x` or `y` in `aes()` has no effect — ggpop ignores them and issues a warning. Leave those aesthetics unmapped.

::: {.callout-warning}
## This will warn (and x/y are silently ignored)
```r
geom_pop(data = df, aes(icon = icon, group = sex, x = sex, y = sex))
```
:::

```{r}
#| label: tip5
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
df_tip5 <- data.frame(
  type = rep(c("Urban", "Rural"), each = 25),
  icon = rep(c("building", "tree"), each = 25),
  stringsAsFactors = FALSE
)

# Correct: no x or y in aes() — geom_pop() handles layout automatically
ggplot() +
  geom_pop(
    data = df_tip5,
    aes(icon = icon, color = type),
    size = 3, dpi = 100, legend_icons = TRUE
  ) +
  scale_color_manual(values = c("Urban" = "#5C6BC0", "Rural" = "#388E3C")) +
  theme_pop() +
  scale_legend_icon(size = 8) +
  labs(title = "Tip 5: No x/y mapping needed in geom_pop()", color = "Area")
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 6 — One icon per legend group when using `legend_icons = TRUE`

When `legend_icons = TRUE`, ggpop reads the first icon from each group to render in the legend. If a single group contains **multiple different icons**, ggpop issues a warning because it can only show one icon per legend key.

**Ensure each value of your `color` grouping variable maps to exactly one icon name.**

```{r}
#| label: tip6
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
# Each group maps to exactly one icon — clean legend
df_tip6 <- data.frame(
  species = rep(c("Birds", "Fish", "Trees"), each = 20),
  icon    = rep(c("dove", "fish", "tree"), each = 20),
  stringsAsFactors = FALSE
)

ggplot() +
  geom_pop(
    data = df_tip6,
    aes(icon = icon, color = species),
    size = 3, dpi = 100,
    legend_icons = TRUE            # one icon per group ✓ — no warning
  ) +
  scale_color_manual(values = c(
    "Birds" = "#0277BD",
    "Fish"  = "#00897B",
    "Trees" = "#2E7D32"
  )) +
  theme_pop() +
  scale_legend_icon(size = 8) +
  labs(title = "Tip 6: One icon per legend group", color = "Species")
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 7 — `scale_legend_icon()` must come after all theme calls

`scale_legend_icon()` intercepts ggplot2's theme system to resize legend keys. If a `theme()` or `theme_*()` call appears **after** `scale_legend_icon()`, it can reset the legend key size and break the sizing.

**Rule:** all `theme_pop()`, `theme_minimal()`, `theme()` calls must precede `scale_legend_icon()`.

::: {.callout-important}
## Wrong order — theme() after scale_legend_icon() resets key size
```r
ggplot(...) +
  geom_pop(...) +
  scale_legend_icon(size = 10) +   # ← scale_legend_icon first
  theme_pop()                       # ← then theme — WRONG
```
:::

```{r}
#| label: tip7
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
df_tip7 <- data.frame(
  status = rep(c("Active", "Inactive"), each = 25),
  icon   = rep(c("circle-check", "circle-xmark"), each = 25),
  stringsAsFactors = FALSE
)

# Correct order: theme calls BEFORE scale_legend_icon()
ggplot(data = df_tip7,
    aes(icon = icon, color = status)) +
  geom_pop(size = 3, dpi = 100, legend_icons = TRUE) +
  scale_color_manual(values = c("Active" = "#2E7D32", "Inactive" = "#C62828")) +
  theme_pop() +                     # ← theme first  ✓
  theme(legend.position = "bottom") +
  scale_legend_icon(size = 10) +    # ← scale_legend_icon last  ✓
  labs(
    title    = "Tip 7: Correct layer order",
    subtitle = "theme calls → scale_legend_icon()",
    color    = "Status"
  )
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 8 — Use `process_data()` to convert count data

If your data has one row per group with a **count column** (not one row per icon), use `process_data()` to expand it. It handles proportional sampling, reproducibility, and returns one row per icon — ready for `geom_pop()`.

```{r}
#| label: tip8
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
# Your raw count data
df_counts_raw <- data.frame(
  education = c("No degree", "High school", "Bachelor's", "Graduate"),
  population = c(12500000, 38000000, 45000000, 18000000)
)

# Expand to one row per icon
df_edu <- process_data(
  data        = df_counts_raw,
  group_var   = education,
  sum_var     = population,
  sample_size = 100
) %>%
  mutate(icon = case_when(
    type == "No degree"   ~ "xmark",
    type == "High school" ~ "school",
    type == "Bachelor's"  ~ "graduation-cap",
    type == "Graduate"    ~ "user-graduate"
  ))

df_edu$type <- factor(df_edu$type,
  levels = c("No degree", "High school", "Bachelor's", "Graduate"))

ggplot(data = df_edu, aes(icon = icon, color = type)) +
  geom_pop(size = 2, dpi = 100, legend_icons = TRUE, arrange = TRUE) +
  scale_color_manual(values = c(
    "No degree"   = "#B71C1C",
    "High school" = "#E65100",
    "Bachelor's"  = "#1565C0",
    "Graduate"    = "#1B5E20"
  )) +
  theme_pop() +
  scale_legend_icon(size = 6) +
  labs(
    title    = "Tip 8: Use process_data() for count-based data",
    subtitle = "Each icon ≈ 1% of the total population sample",
    color    = "Education"
  )
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 9 — Use `seed` for reproducible charts

`geom_pop()` uses randomness when placing icons across the grid. This means that every time you run the same code, the exact icon layout may differ slightly — which can be a problem in reports, papers, or automated pipelines where you need consistent output.

Pass a `seed` argument directly to `geom_pop()` to lock the randomness. Any integer works; the same seed always produces the same layout.

::: {.callout-tip}
## Why this matters
If you are including a chart in a paper, dashboard, or automated report, you want the output to be **identical every time** the code runs. A fixed seed guarantees that.
:::

```{r}
#| label: tip9
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
df_tip9_raw <- data.frame(
  source     = c("Coal", "Natural Gas", "Nuclear", "Renewables"),
  generation = c(800000, 1600000, 700000, 900000)
)

df_tip9 <- process_data(
  data        = df_tip9_raw,
  group_var   = source,
  sum_var     = generation,
  sample_size = 100
) %>%
  mutate(icon = case_when(
    type == "Coal"        ~ "industry",
    type == "Natural Gas" ~ "fire",
    type == "Nuclear"     ~ "atom",
    type == "Renewables"  ~ "sun"
  ))

ggplot(data = df_tip9, aes(icon = icon, color = type)) +
  geom_pop(size = 2, dpi = 100, seed = 42) +
  scale_color_manual(values = c(
    "Coal"        = "#B0BEC5",
    "Natural Gas" = "#FFB74D",
    "Nuclear"     = "#CE93D8",
    "Renewables"  = "#4DB6AC"
  )) +
  theme_pop() +
  scale_legend_icon(size = 8) +
  labs(
    title    = "U.S. Electricity Generation by Source",
    subtitle = "Each icon represents ~1% of total generation — layout fixed with seed = 42",
    color    = "Energy source"
  )
```
