---
title: "Custom SVG Icons"
format:
  html:
    code-fold: true
    code-summary: "Show the code"
---

```{r}
#| label: setup
#| include: false
#| message: false
#| warning: false

library(ggpop)
library(ggplot2)
```

ggpop resolves every icon name through a four-step priority chain:

1. **Local `.svg` path** — a bare file path ending in `.svg`
2. **`icon_path` folder** — bare name looked up inside a user-supplied directory
3. **Bundled ggpop marker** — one of the 14 solid/outline markers shipped with the package
4. **Font Awesome** — any valid FA name (the default for most icons)

The chain stops at the first match, so your files always take priority over
Font Awesome names.

## Bundled markers

ggpop ships 14 geometric markers you can use by name with no folder needed.
List them with `ggpop_markers()`:

```{r}
#| label: bundled-list
#| code-fold: false
ggpop_markers()$bundled
```

They work anywhere an icon name is expected — in `geom_icon_point()`,
`geom_pop()`, and `marker_legend()`.

```{r}
#| label: fig-bundled
#| message: false
#| warning: false
#| fig-width: 9
#| fig-height: 2.2
#| fig-cap: "All 14 bundled markers rendered with `geom_icon_point()`."

families <- c("square", "circle", "diamond")
variants <- c("inset", "hollow", "cross", "solid")
pal <- c(square = "#1E88E5", circle = "#2A9D8F", diamond = "#E76F51")

icons <- paste(rep(families, each = 4), variants, sep = "-")
df_markers <- data.frame(
  icon   = c(icons, "plus-bold", "triangle-down"),
  x      = seq_len(14),
  y      = 1,
  colour = c(
    rep(pal["square"],  4),
    rep(pal["circle"],  4),
    rep(pal["diamond"], 4),
    "#6D6875", "#6D6875"
  ),
  stringsAsFactors = FALSE
)

ggplot(df_markers, aes(x = x, y = y, icon = icon, colour = colour)) +
  geom_icon_point(size = 8, dpi = 150, legend_icons = FALSE) +
  geom_text(aes(label = icon), y = 0.55, angle = 50,
            hjust = 1, size = 3, colour = "grey30") +
  scale_colour_identity() +
  scale_x_continuous(expand = expansion(add = c(0.8, 0.5))) +
  scale_y_continuous(limits = c(0.2, 1.4)) +
  theme_void()
```

## Using your own SVG files

Place your `.svg` files in a folder and pass the path via `icon_path`. Reference
each file by its bare name (no `.svg` extension):

```{r}
#| label: icon-path-example
#| eval: false
#| code-fold: false

# Folder layout:
#   my-icons/
#     hospital.svg
#     clinic.svg
#     pharmacy.svg

ggplot(df, aes(x = x, y = y, icon = facility_type, colour = region)) +
  geom_icon_point(size = 5, icon_path = "my-icons/") +
  scale_colour_manual(values = pal)
```

Set `options(ggpop.icon_path = "my-icons/")` once per session to avoid
repeating `icon_path` in every call:

```{r}
#| label: global-option
#| eval: false
#| code-fold: false

options(ggpop.icon_path = "~/my-icons/")

# All three calls now resolve from ~/my-icons/ automatically
ggplot(df1, aes(x, y, icon = type)) + geom_icon_point()
ggplot(df2, aes(x, y, icon = type)) + geom_icon_point()
```

## Mixing icon sources

Sources can be mixed in a single plot — each `icon` value resolves
independently through the chain:

```{r}
#| label: mixed-sources
#| eval: false
#| code-fold: false

df_mixed <- data.frame(
  x    = 1:3,
  y    = 1,
  icon = c("hospital.svg",   # local absolute path  → resolves at step 1
            "square-solid",  # bundled marker       → resolves at step 3
            "stethoscope"),  # Font Awesome name     → resolves at step 4
  stringsAsFactors = FALSE
)

ggplot(df_mixed, aes(x = x, y = y, icon = icon)) +
  geom_icon_point(size = 6, icon_path = "my-icons/")
```

## Name shadowing

If a file in your `icon_path` folder shares a name with a Font Awesome icon
(e.g. `car.svg`), ggpop warns you at construction time:

```{r}
#| label: shadow-warning
#| eval: false
#| code-fold: false

# ~/my-icons/ contains car.svg and bus.svg — both are FA names
geom_icon_point(icon_path = "~/my-icons/")
#> Warning: 2 icon names in `icon_path` shadow Font Awesome names.
#> x Shadowed: "car", "bus".
#> i These will resolve to your SVG files, not Font Awesome icons.
#> i Rename the files (e.g. `my-car.svg`) to avoid the conflict.
```

The warning fires once at layer construction and is silent when there are no
conflicts.

## SVG tips

- **Single colour** — ggpop recolours icons by replacing the fill. Multi-colour
  SVGs will have all fills replaced by the mapped colour.
- **No embedded raster** — keep SVGs as pure vector paths; embedded PNGs inside
  SVGs are not recoloured.
- **`viewBox` required** — make sure your SVG has a `viewBox` attribute so
  ggpop can scale it correctly.
- **Naming** — avoid naming files the same as Font Awesome icons unless you
  intentionally want to override them.
