---
title: "Icon Legends: Native Guides and Standalone Composites"
format:
  html:
    code-fold: true
    code-summary: "Show the code"
---

```{r}
#| label: setup
#| include: false
#| message: false
#| warning: false

library(ggpop)
library(ggplot2)
library(dplyr)
```

ggpop gives you two ways to build a legend, and picking the right one keeps your
code short:

1. **Native icon legends** - for a legend keyed to your plot's data. ggplot2
   builds it for you; you only switch the keys to icons. This is what you want
   almost every time.
2. **Standalone composite legends** - for a legend that is really a small
   annotated figure, decoupled from any plot (multiple grouped columns, mixed
   symbology, fixed pixel dimensions). ggplot2's guide system cannot express
   these, so `marker_legend()` draws them for you.

## The common case: native icon legends

Map an aesthetic, set `legend_icons = TRUE`, and let ggplot2 do the rest. The
icon keys are drawn by ggpop's custom key glyph and recoloured to match each
group; `scale_legend_icon()` sizes them.

```{r}
#| label: fig-native
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 3.6
#| fig-cap: "A native icon legend - ggplot2 builds the guide, ggpop draws the keys."

df_modes <- data.frame(
  x     = c(1, 2, 3, 4, 5, 6, 7, 8),
  y     = c(1, 2, 1, 2, 1, 2, 1, 2),
  group = c("Car", "Bus", "Subway", "Bicycle", "Plane", "Ferry", "Truck", "Walking"),
  icon  = c("car", "bus", "train-subway", "bicycle", "plane", "ship", "truck", "person-walking"),
  stringsAsFactors = FALSE
)
df_modes$group <- factor(df_modes$group, levels = df_modes$group)

col_map <- c(
  Car = "#E41A1C", Bus = "#377EB8", Subway = "#4DAF4A", Bicycle = "#984EA3",
  Plane = "#FF7F00", Ferry = "#009E9E", Truck = "#A65628", Walking = "#666666"
)

ggplot(df_modes, aes(x = x, y = y, icon = icon, colour = group)) +
  geom_icon_point(size = 6, dpi = 120, legend_icons = TRUE) +
  scale_colour_manual(values = col_map) +
  coord_cartesian(ylim = c(0.5, 2.6), clip = "off") +
  scale_legend_icon(size = 6) +
  theme_minimal()
```

::: {.callout-tip}
For any legend tied to your data, stop here. The native path stays in sync with
your scales automatically and needs no manual layout. Reach for
`marker_legend()` only when you need a standalone composite that ggplot2 guides
cannot produce.
:::

One ordering rule: `scale_legend_icon()` must come **after** any `theme()` call,
because a later `theme()` resets the legend key size.

## Markers beyond Font Awesome

The `icon` aesthetic accepts more than Font Awesome names. ggpop ships a set of
bundled markers, and you can register a folder of your own `.svg` files. List
what is available with `ggpop_markers()`:

```{r}
#| label: markers
#| code-fold: false
ggpop_markers()$bundled
```

These names work anywhere an icon is expected - in the geoms above and in the
composite legends below. To use your own SVGs, pass a folder via `icon_path` (or
set `options(ggpop.icon_path = "path/to/svgs")`) and reference each file by its
bare name.

## Standalone composite legends with `marker_legend()`

When a legend needs multiple grouped columns, mixed symbology, and a fixed size -
the kind of figure often exported as a standalone image - ggplot2's guide system
falls short. `marker_legend()` takes a tidy data frame of `icon` + `label`
(+ optional per-row `colour` and `column`) and lays it out for you.

### A Font Awesome composite

No bundled markers required - any icon source works, including mixed sources in
one legend.

```{r}
#| label: fig-composite-fa
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 2.6
#| fig-cap: "A two-column composite legend built entirely from Font Awesome icons."

df_legend <- data.frame(
  column = c(1, 1, 1, 2, 2, 2),
  icon   = c("car", "bus", "bicycle", "plane", "ship", "truck"),
  label  = c("Car", "Bus", "Bicycle", "Plane", "Ferry", "Truck"),
  colour = c("#E41A1C", "#377EB8", "#984EA3", "#FF7F00", "#009E9E", "#A65628"),
  stringsAsFactors = FALSE
)

marker_legend(
  df_legend,
  title = "Transport modes",
  marker_size = 5, label_size = 4, col_spacing = 14, label_gap = 1.6
)
```

### Multi-column composite legend

This is the use case `marker_legend()` exists for: a multi-column legend that
encodes two semantic dimensions simultaneously — here, region type (colour) and
indicator domain (column) — using bundled markers to distinguish subcategories.

```{r}
#| label: fig-composite-health
#| message: false
#| warning: false
#| fig-width: 9.5
#| fig-height: 2.2
#| fig-cap: "A standalone composite legend encoding region type and health indicator domain."

blue <- "#1E88E5"
teal <- "#2A9D8F"

df_legend <- rbind(
  data.frame(
    column = 1, colour = blue,
    icon  = c("square-inset", "square-hollow", "square-cross", "square-solid"),
    label = c("Urban — Excellent", "Urban — Good",
              "Urban — Fair",     "Urban — Poor")
  ),
  data.frame(
    column = 2, colour = teal,
    icon  = c("circle-inset", "circle-hollow", "circle-cross", "circle-solid"),
    label = c("Rural — Excellent", "Rural — Good",
              "Rural — Fair",     "Rural — Poor")
  ),
  data.frame(
    column = 3, colour = teal,
    icon  = c("diamond-inset", "diamond-hollow", "diamond-cross", "diamond-solid"),
    label = c("Remote — Excellent", "Remote — Good",
              "Remote — Fair",      "Remote — Poor")
  ),
  stringsAsFactors = FALSE
)

marker_legend(
  df_legend,
  marker_size = 5, label_size = 4, dpi = 200,
  col_spacing = 3, row_spacing = 0.8, label_gap = 0.4
) +
  coord_cartesian(xlim = c(-0.6, 8.5), ylim = c(-3.2, 0.48), clip = "off")
```

::: {.callout-note}
`marker_legend()` returns a plain `ggplot`. Add `ggplot2::annotate()` layers for
extra symbols or labels, then export at exact pixel dimensions with
`ggplot2::ggsave(width = W / 300, height = H / 300, dpi = 300)`.
:::

## Composite legends built from a data frame: `legend_canvas()`

`marker_legend()` above lays out one flat list of icon + label rows. Some
legends need more structure than that - an icon grid crossed by two
dimensions, a block of colour tiles for a grouping variable, and a small key
for extra symbols (a trend line, a shaded band, a flagged point) - all in one
figure. `legend_canvas()` builds exactly that from a single tidy data frame,
`df_legend`, where a `type` column tells it what to draw:

| `type`   | Renders as                     | Lives in                              |
|:---------|:--------------------------------|:----------------------------------------|
| `icon`   | An icon marker at `row`/`col`   | `grid_section`                          |
| `swatch` | A filled rectangle              | `group_section` or `symbol_section`     |
| `line`   | A short line segment            | `symbol_section`                        |
| `point`  | A bold glyph (default `"*"`)    | `symbol_section`                        |

`icon`-typed rows always render as icons no matter what `type` says - the
value is a bookkeeping label there, not a switch. `swatch`/`line`/`point` are
the only values `key_legend()` actually dispatches on, and that dispatch is
the only place a new type could be added.

### Deriving the icon grid from data with `icon_grid()`

If your icon-grid combinations already exist in a data frame - say, one row
per package-size / distance-zone combination - `icon_grid()` derives the
unique `row`/`col` positions for you instead of typing them by hand. Factor
columns keep a deliberate row/col order; unordered columns sort automatically.

```{r}
#| label: icon-grid-derive
#| code-fold: false

df_plans <- data.frame(
  size     = factor(c("Small", "Small", "Large", "Large"), levels = c("Small", "Large")),
  distance = factor(c("Local", "National", "Local", "National"), levels = c("Local", "National")),
  icon     = c("square-hollow", "square-solid", "circle-hollow", "circle-solid"),
  stringsAsFactors = FALSE
)
df_plans$cell_label <- paste0(
  substr(df_plans$size, 1, 1), "-",
  c(Local = "Loc", National = "Natl")[as.character(df_plans$distance)]
)

df_grid <- icon_grid(
  df_plans, icon = "icon", label = "cell_label",
  row = "size", col = "distance"
)
df_grid
```

### Assembling grid + group + symbol sections

Combine that grid with a colour-tile group (`group_section`) and a small
symbol key (`symbol_section`) by `rbind()`-ing three data frames that share
`section`/`type`/`label`/`color` columns:

```{r}
#| label: fig-legend-canvas
#| message: false
#| warning: false
#| fig-width: 9.5
#| fig-height: 2
#| fig-cap: "A grid + group + symbol composite legend built from one df_legend data frame."

plan_colours <- c(Standard = "#8D99AE", Express = "#EF476F")

df_legend <- rbind(
  df_grid,
  data.frame(
    section = "plan", type = "swatch",
    label = names(plan_colours), color = unname(plan_colours),
    icon = NA, row = NA, col = NA
  ),
  data.frame(
    section = "value", type = c("line", "swatch", "point"),
    label   = c("Best-value frontier", "Acceptable range", "Best pick"),
    color   = c("black", "grey75", "black"),
    icon = NA, row = NA, col = NA
  )
)

legend_canvas(
  df_legend,
  grid_title       = "Package size × distance zone",
  group_section    = "plan", group_title = "Plan", group_width = 0.9, group_gap = 0.3,
  symbol_section   = "value", symbol_right_gap = 0.8, symbol_key_width = 0.5,
  col_spacing = 2.2, row_spacing = 1.2, label_gap = 0.15,
  marker_size = 5, label_size = 3.6, dpi = 150
)
```

::: {.callout-tip}
`group_title` lets the displayed heading differ from the `section` value used
to match rows - keep `section` values plain and lowercase (`"plan"`) while the
on-plot title stays capitalised (`"Plan"`). `grid_section` and `grid_title`
work the same way for the icon grid.
:::

Column spacing has to leave room for your longest label in that column before
the next section starts - if sections start overlapping, widen `col_spacing`,
`group_width`, or `symbol_right_gap` rather than shortening labels first.

## One call for the whole thing: `legend_composite()`

`legend_canvas()` gives you every knob, but for the standard grid + group +
symbol legend you end up repeating the same spacing, sizing, and centring
numbers on every figure. `legend_composite()` is the opinionated wrapper: hand
it the same `df_legend` and the physical strip size, and it applies a fixed
proportion ladder (`legend_ratios()`), centres the content, and fits a tight
border with `legend_box()` - the whole legend from one call.

```{r}
#| label: fig-legend-composite
#| message: false
#| warning: false
#| fig-width: 11
#| fig-height: 1.7
#| fig-cap: "The same three-section df_legend, rendered in one legend_composite() call with a fitted border."

legend_composite(
  df_legend,
  width = 11, height = 1.7,
  grid_title     = "Size and zone",
  group_section  = "plan", group_title = "Plan",
  symbol_section = "value",
  ratios = modifyList(legend_ratios(), list(col_spacing = 1.5, symbol_right_gap = 1.4))
)
```

Instead of hand-setting `col_spacing`, `group_width`, `marker_size`,
`label_size`, and the rest, you give `legend_composite()` the physical
`width`/`height` and it derives every length from three base sizes and the
ratio ladder. You usually touch nothing but the titles; when a section needs
more room - here the two-column grid's title and the wide symbol labels -
override a single rung with `ratios = modifyList(legend_ratios(), ...)`.

### The same proportions at any figure width

The base sizes are calibrated for a `base_width`-inch strip (default 27) and
multiplied by `width / base_width`, so passing your actual `width` reproduces
the identical legend at that physical size - no per-figure retuning. Halve the
width and text, markers, spacing, and border all scale together. Set
`base_width = width` to opt out and size in absolute units instead.

::: {.callout-tip}
Keep sparse legends compact - do not stretch them. `content_range` sets how
much horizontal room the content is centred in. A dense legend (many columns,
long labels) fills a wide strip on its own; a sparse one should stay compact.
Leave `content_range` at its default rather than shrinking it to force the
content to fill the width - the colour swatches are drawn in data coordinates,
so a small `content_range` stretches them into wide banners while the
fixed-size icons stay put. `legend_composite()` warns when the swatches get
that lopsided so you catch it early.
:::

The grid's `icon` column resolves per row, so one grid can mix Font Awesome
names, bundled ggpop markers, and your own `.svg` files in a single legend -
see [Custom SVG icons](custom-svg-icons.html).

## Stacking a plot and its legend with `legend_strip()`

The composite above is a self-contained `ggplot`. To pin it under a real plot
in one exported figure - rather than a standalone panel - add it with
`legend_strip(strip_plot, height)`:

```{r}
#| label: fig-legend-strip
#| message: false
#| warning: false
#| fig-width: 9.5
#| fig-height: 5.5
#| fig-cap: "A scatter plot with its legend_canvas() legend stacked directly below it."

df_points <- data.frame(
  cost = c(4, 6, 9, 14, 7, 11, 16, 22),
  days = c(6, 4, 2, 1, 5, 3, 1.5, 1),
  plan = c("Standard", "Standard", "Express", "Express",
           "Standard", "Standard", "Express", "Express")
)

p_main <- ggplot(df_points, aes(x = cost, y = days, colour = plan)) +
  geom_point(size = 3) +
  scale_colour_manual(values = plan_colours, guide = "none") +
  scale_x_continuous("Cost ($)") +
  scale_y_continuous("Delivery time (days)") +
  ggtitle("Cost vs. delivery time") +
  theme_classic(base_size = 13) +
  theme(axis.line.x = element_blank())

p_legend <- legend_canvas(
  df_legend,
  grid_title       = "Package size × distance zone",
  group_section    = "plan", group_title = "Plan", group_width = 0.9, group_gap = 0.3,
  symbol_section   = "value", symbol_right_gap = 0.8, symbol_key_width = 0.5,
  col_spacing = 2.2, row_spacing = 1.2, label_gap = 0.15,
  marker_size = 5, label_size = 3.6, dpi = 150
)

p_main + legend_strip(p_legend, height = 1.4)
```

::: {.callout-tip}
`height` is a physical size in inches, independent of the main plot's own
aspect ratio - set it once and `ggsave(width =, height =)` on the combined
figure exactly like any other `ggplot`. Dropping `theme_classic()`'s bottom
`axis.line` (as above) avoids a redundant rule sitting right above the
legend - keep the left axis line, drop only `axis.line.x`.
:::
