---
title: "Icon Legends: Native Guides and Standalone Composites"
format:
  html:
    code-fold: false
    code-summary: "Show the code"
---

```{r}
#| label: setup
#| include: false
#| message: false
#| warning: false

library(ggpop)
library(ggplot2)
library(dplyr)
```

ggpop gives you two ways to build a legend, and picking the right one keeps your
code short:

1. **Native icon legends** - for a legend keyed to your plot's data. ggplot2
   builds it for you; you only switch the keys to icons. This is what you want
   almost every time.
2. **Standalone composite legends** - for a legend that is really a small
   annotated figure, decoupled from any plot (multiple grouped columns, mixed
   symbology, fixed pixel dimensions). ggplot2's guide system cannot express
   these, so `marker_legend()` draws them for you.

## The common case: native icon legends

Map an aesthetic, set `legend_icons = TRUE`, and let ggplot2 do the rest. The
icon keys are drawn by ggpop's custom key glyph and recoloured to match each
group; `scale_legend_icon()` sizes them.

```{r}
#| label: fig-native
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 3.6
#| fig-cap: "A native icon legend - ggplot2 builds the guide, ggpop draws the keys."

df_modes <- data.frame(
  x     = c(1, 2, 3, 4, 5, 6, 7, 8),
  y     = c(1, 2, 1, 2, 1, 2, 1, 2),
  group = c("Car", "Bus", "Subway", "Bicycle", "Plane", "Ferry", "Truck", "Walking"),
  icon  = c("car", "bus", "train-subway", "bicycle", "plane", "ship", "truck", "person-walking"),
  stringsAsFactors = FALSE
)
df_modes$group <- factor(df_modes$group, levels = df_modes$group)

col_map <- c(
  Car = "#E41A1C", Bus = "#377EB8", Subway = "#4DAF4A", Bicycle = "#984EA3",
  Plane = "#FF7F00", Ferry = "#009E9E", Truck = "#A65628", Walking = "#666666"
)

ggplot(df_modes, aes(x = x, y = y, icon = icon, colour = group)) +
  geom_icon_point(size = 6, dpi = 120, legend_icons = TRUE) +
  scale_colour_manual(values = col_map) +
  scale_legend_icon(size = 6) +
  theme_minimal()
```

::: {.callout-tip}
For any legend tied to your data, stop here. The native path stays in sync with
your scales automatically and needs no manual layout. Reach for
`marker_legend()` only when you need a standalone composite that ggplot2 guides
cannot produce.
:::

One ordering rule: `scale_legend_icon()` must come **after** any `theme()` call,
because a later `theme()` resets the legend key size.

## Markers beyond Font Awesome

The `icon` aesthetic accepts more than Font Awesome names. ggpop ships a set of
bundled markers, and you can register a folder of your own `.svg` files. List
what is available with `ggpop_markers()`:

```{r}
#| label: markers
ggpop_markers()$bundled
```

These names work anywhere an icon is expected - in the geoms above and in the
composite legends below. To use your own SVGs, pass a folder via `icon_path` (or
set `options(ggpop.icon_path = "path/to/svgs")`) and reference each file by its
bare name.

## Standalone composite legends with `marker_legend()`

When a legend needs multiple grouped columns, mixed symbology, and a fixed size -
the kind of figure often exported as a standalone image - ggplot2's guide system
falls short. `marker_legend()` takes a tidy data frame of `icon` + `label`
(+ optional per-row `colour` and `column`) and lays it out for you.

### A Font Awesome composite

No bundled markers required - any icon source works, including mixed sources in
one legend.

```{r}
#| label: fig-composite-fa
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 2.6
#| fig-cap: "A two-column composite legend built entirely from Font Awesome icons."

df_legend <- data.frame(
  column = c(1, 1, 1, 2, 2, 2),
  icon   = c("car", "bus", "bicycle", "plane", "ship", "truck"),
  label  = c("Car", "Bus", "Bicycle", "Plane", "Ferry", "Truck"),
  colour = c("#E41A1C", "#377EB8", "#984EA3", "#FF7F00", "#009E9E", "#A65628"),
  stringsAsFactors = FALSE
)

marker_legend(
  df_legend,
  title = "Transport modes",
  marker_size = 5, label_size = 4, col_spacing = 14, label_gap = 1.6
)
```

### Reproducing a screening-strategy legend

This is the use case `marker_legend()` exists for: a multi-column legend of
bundled markers in two semantic colours, extended with `annotate()` for the
frontier and near-efficient symbols, and exported at a fixed size.

```{r}
#| label: fig-composite-sda
#| message: false
#| warning: false
#| fig-width: 10.8
#| fig-height: 1.4
#| fig-cap: "A standalone screening-strategy legend, reproduced in ggplot + ggpop."

pink  <- "#FF1493"
green <- "#006400"

df_sda <- rbind(
  data.frame(
    column = 1, colour = pink,
    icon  = c("square-inset", "circle-hollow", "square-cross", "circle-solid"),
    label = c("FIT 45-49y, COL 50-70y", "FIT 50-54y, COL 55-75y",
              "FIT 45-49y, COL 50-80y", "FIT 50-54y, COL 55-85y")
  ),
  data.frame(
    column = 2, colour = green,
    icon  = c("square-inset", "square-hollow", "square-cross", "square-solid"),
    label = c("COL 45y, FIT 55-70y", "COL 45y, FIT 55-75y",
              "COL 45y, FIT 55-80y", "COL 45y, FIT 55-85y")
  ),
  data.frame(
    column = 3, colour = green,
    icon  = c("circle-inset", "circle-hollow", "circle-cross", "circle-solid"),
    label = c("COL 50y, FIT 60-70y", "COL 50y, FIT 60-75y",
              "COL 50y, FIT 60-80y", "COL 50y, FIT 60-85y")
  ),
  stringsAsFactors = FALSE
)

marker_legend(
  df_sda,
  marker_size = 3, label_size = 2.4, dpi = 200, col_spacing = 13
)
```

::: {.callout-note}
`marker_legend()` returns a plain `ggplot`. Add `ggplot2::annotate()` layers for
extra symbols (frontier segments, grey bands, asterisks), then export at exact
pixel dimensions with `ggplot2::ggsave(width = W / 300, height = H / 300, dpi = 300)`.
:::
