---
title: "New to R? Start Here"
format:
  html:
    code-fold: false
    code-summary: "Show the code"
---

```{r}
#| label: setup
#| include: false
#| message: false
#| warning: false
library(ggpop)
library(ggplot2)
```

A guide for complete beginners. No math or programming experience required — just follow along.

<div style="line-height: 0.6;"><br></div>

---

## What is R?

R is a free programming language designed for working with data. Think of it as a very powerful calculator that can also draw charts, run statistics, and handle millions of rows of information.

Why R works for beginners:

- It's **free** and runs on Windows, Mac, and Linux
- It has thousands of **packages** (ready-made tools built by other people)
- A large community — your questions are likely already answered online
- It's used by scientists, journalists, economists, and data analysts around the world

<div style="line-height: 0.6;"><br></div>

---

## Step 0 — Install R and RStudio

Before anything else, you need two free programs:

1. **R** — the language itself. Download from [cran.r-project.org](https://cran.r-project.org/)
2. **RStudio** — a friendly interface for writing R code. Download from [posit.co/download/rstudio-desktop](https://posit.co/download/rstudio-desktop/)

Install R, then RStudio. The **Console** (bottom-left) is where you type commands.

::: {.callout-tip}
## Think of it like this
R is the engine. RStudio is the car. You drive the car, not the engine directly.
:::

<div style="line-height: 0.6;"><br></div>

---

## Step 1 — Your first commands

Click inside the Console and type the following. Press **Enter** after each line.

```{r}
#| label: first-commands
#| eval: false

# R can be used as a calculator
2 + 2
10 * 5
100 / 4
```

```{r}
#| label: first-commands-run
#| echo: false
2 + 2
10 * 5
100 / 4
```

The `#` symbol starts a **comment** — R ignores anything after it.

<div style="line-height: 0.6;"><br></div>

### Saving values with `<-`

Instead of re-typing numbers every time, you can save them into a **variable** using the arrow `<-`:

```{r}
#| label: variables

my_number <- 42
my_name   <- "Jorge"

my_number
my_name
```

Now `my_number` holds the value `42`. You can use it anywhere:

```{r}
#| label: variables-use
my_number * 2
```

::: {.callout-tip}
## Naming variables
Use descriptive names with underscores: `population_2024`, `total_cats`. Avoid spaces and special characters. R is case-sensitive: `MyData` and `mydata` are different things.
:::

<div style="line-height: 0.6;"><br></div>

---

## Step 2 — Understanding data frames

In R, data lives in **data frames** — think of them as spreadsheets with rows and columns. Each column is a variable (like "city" or "population"), and each row is one observation.

Here's how to create a simple data frame:

```{r}
#| label: dataframe

df_cities <- data.frame(
  city       = c("Paris", "Tokyo", "Cairo", "Lagos"),
  population = c(2161000, 13960000, 22183000, 15387639)
)

df_cities
```

`data.frame()` creates a table. `c()` combines values into a column. Commas separate columns.

You can access a single column using `$`:

```{r}
#| label: column-access
df_cities$city
df_cities$population
```

<div style="line-height: 0.6;"><br></div>

---

## Step 3 — Installing packages

R's power comes from **packages** — collections of extra functions. Install once, load every session.

```{r}
#| label: install-packages
#| eval: false

# Install packages (do this once)
install.packages("ggplot2")
install.packages("ggpop")

# Load packages (do this every time you open RStudio)
library(ggplot2)
library(ggpop)
```

::: {.callout-tip}
## The difference between install and library
`install.packages()` downloads once. `library()` loads per session.
:::

<div style="line-height: 0.6;"><br></div>

---

## Step 4 — Your first chart with ggplot2

First, a simple ggplot2 chart to understand the structure:

We'll use data about how people in a city get to work. Imagine we surveyed 100 commuters:

```{r}
#| label: commuter-summary

df_transport <- data.frame(
  transport = c("Car", "Subway", "Bike", "Walk"),
  count     = c(45, 30, 15, 10)
)

df_transport
```

Now let's make a bar chart:

```{r}
#| label: bar-chart
#| fig-width: 10
#| fig-height: 9
#| message: false
#| warning: false

library(ggplot2)

ggplot(data = df_transport, aes(x = transport, y = count, fill = transport)) +
  geom_bar(stat = "identity") +
  labs(
    title    = "How Do People Get to Work?",
    subtitle = "Survey of 100 commuters",
    x        = "Transport mode",
    y        = "Number of people",
    fill     = "Transport"
  ) +
  theme_minimal()
```

Let's read the code line by line:

| Code | What it does |
|:---|:---|
| `ggplot(data = ..., aes(...))` | Creates the canvas and maps columns to visual properties |
| `aes(x = transport, y = count, fill = transport)` | `x` = horizontal axis, `y` = bar height, `fill` = bar color |
| `geom_bar(stat = "identity")` | Draws the bars (use `"identity"` when your data already has the counts) |
| `labs(...)` | Adds titles and axis labels |
| `theme_minimal()` | Applies a clean, minimal style |

ggplot2 builds charts by layering pieces with `+`.

<div style="line-height: 0.6;"><br></div>

---

## Step 5 — Upgrade to ggpop

`ggpop` replaces bars with icons — each person becomes visible. Let's recreate this:

First, we build a data frame with **one row per person** (instead of one row per group):

```{r}
#| label: commuter-data

df_commuters <- data.frame(
  transport = c(
    rep("Car",    45),
    rep("Subway", 30),
    rep("Bike",   15),
    rep("Walk",   10)
  ),
  icon = c(
    rep("car",            45),
    rep("train-subway",   30),
    rep("bicycle",        15),
    rep("person-walking", 10)
  )
)
```

`rep("Car", 45)` creates 45 rows — one per commuter. `icon` holds the Font Awesome name.

Now the chart:

```{r}
#| label: geom-pop-chart
#| fig-width: 10
#| fig-height: 9
#| message: false
#| warning: false

library(ggpop)

ggplot(data = df_commuters, aes(icon = icon, color = transport)) +
  geom_pop(size = 2, dpi  = 100, legend_icons = TRUE) +
  scale_color_manual(values = c(
    "Car"    = "#E64A19",
    "Subway" = "#1565C0",
    "Bike"   = "#2E7D32",
    "Walk"   = "#6A1B9A"
  )) +
  theme_pop() +
  scale_legend_icon(size = 7) +
  labs(
    title    = "How Do People Get to Work?",
    subtitle = "Each icon represents one commuter out of 100 surveyed",
    color    = "Transport"
  )
```

Same structure as ggplot2, but each data point is visible as an icon.

::: {.callout-tip}
## Finding icon names
Use `fa_icons()` to search the library of 2,000+ free icons:

```r
fa_icons(query = "person")
fa_icons(query = "car")
fa_icons(query = "heart")
```
:::

<div style="line-height: 0.6;"><br></div>

---

## Step 6 — Scatter plots with icons using `geom_icon_point()`

`geom_icon_point()` places icons on a scatter plot — one per data point, no grid.

Let's use a dataset about sleep and performance. We surveyed students on how many hours they slept and their exam score, grouped by their preferred study method:

```{r}
#| label: sleep-data

df_weather <- data.frame(
  temperature = c(15, 18, 22, 25, 28, 30, 32, 30, 27, 24, 20, 16,
                  10, 12, 15, 18, 20, 22, 24, 22, 19, 16, 13, 11,
                  5, 8, 12, 15, 18, 20, 22, 20, 17, 14, 10, 7,
                  28, 30, 32, 35, 36, 38, 40, 38, 35, 33, 30, 28),
  ice_cream_sales = c(20, 25, 35, 45, 55, 65, 75, 70, 60, 50, 35, 25,
                      15, 18, 22, 30, 38, 45, 52, 48, 35, 28, 20, 16,
                      10, 12, 18, 25, 32, 40, 48, 42, 30, 22, 15, 12,
                      70, 75, 80, 90, 95, 100, 110, 105, 95, 85, 75, 70),
  season      = c(
    rep("Spring", 12),
    rep("Winter", 12),
    rep("Autumn", 12),
    rep("Summer", 12)
  ),
  icon        = c(
    rep("seedling", 12),
    rep("snowflake", 12),
    rep("leaf", 12),
    rep("sun", 12)
  )
)

```

Now plot it with `geom_point()`:

```{r}
#| label: geom-icon-point-chart
#| fig-width: 10
#| fig-height: 7
#| message: false

ggplot(
  data = df_weather,
  aes(x = temperature, y = ice_cream_sales, icon = icon, color = season)
) +
  geom_point(size = 2) +
  scale_color_manual(values = c(
    "Spring" = "#81C784",
    "Summer" = "#FFD54F",
    "Autumn" = "#FFB74D",
    "Winter" = "#64B5F6"
  )) +
  scale_legend_icon(size = 9) +
  labs(
    title    = "Temperature vs Ice Cream Sales",
    subtitle = "Sales increase with warmer weather across all four seasons",
    x        = "Temperature (°C)",
    y        = "Ice cream sales (units)",
    color    = "Season"
  ) +
  theme_minimal()

```

Now with `geom_icon_point()`:

```{r}
#| label: geom-point
#| fig-width: 10
#| fig-height: 7
#| message: false

ggplot(
  data = df_weather,
  aes(x = temperature, y = ice_cream_sales, icon = icon, color = season)
) +
  geom_icon_point(size = 2, dpi = 100) +
  scale_color_manual(values = c(
    "Spring" = "#81C784",
    "Summer" = "#FFD54F",
    "Autumn" = "#FFB74D",
    "Winter" = "#64B5F6"
  )) +
  scale_legend_icon(size = 9) +
  labs(
    title    = "Temperature vs Ice Cream Sales",
    subtitle = "Sales increase with warmer weather across all four seasons",
    x        = "Temperature (°C)",
    y        = "Ice cream sales (units)",
    color    = "Season"
  ) +
  theme_minimal()

```


<div style="line-height: 0.6;"><br></div>

---

## Where to go from here

You went from zero to four real charts in R. Here's what to explore next:

| Topic | Where to look |
|:---|:---|
| More `geom_pop()` examples | [Getting Started](getting-started.html) vignette |
| Icon search | [Font Awesome Icons](fa-icons.html) vignette |
| More `geom_icon_point()` examples | [geom_icon_point()](geom-icon-point.html) vignette |
| Colors & themes | [Themes & Customization](themes-customization.html) vignette |
| Common pitfalls | [Tips & Best Practices](tips.html) vignette |

::: {.callout-tip}
## Keep learning R
The best way to learn is to work with data you care about. Find a dataset about something you're interested in — sports, music, health, economics — and try to visualize it.

When stuck, copy the error into a search engine — the R community is helpful.
:::
