---
title: "Tips & Best Practices"
format:
  html:
    code-fold: false
    code-summary: "Show the code"
---

```{r}
#| label: setup
#| include: false
#| message: false
#| warning: false
library(ggpop)
library(ggplot2)
library(dplyr)
```

Essential rules and conventions for using `ggpop`, with working examples.

<div style="line-height: 0.6;"><br></div>

---

## Tip 1 — Use valid Font Awesome icon names

The `icon` column must contain valid Font Awesome names. Use `fa_icons()` to search.

::: {.callout-tip}
## How to find valid icon names
```r
# Search by keyword
fa_icons(query = "person")
fa_icons(query = "car")
fa_icons(query = "heart")
```
:::

```{r}
#| label: tip1
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
#| dev: png
#| dev-args: !expr list(bg = "transparent")

df_tip1 <- data.frame(
  transport = rep(c("Car", "Bicycle", "Plane"), each = 10),
  icon      = rep(c("car", "bicycle", "plane"), each = 10),
  stringsAsFactors = FALSE
)

ggplot() +
  geom_pop(
    data = df_tip1,
    aes(icon = icon, color = transport),
    size = 3, dpi = 100, legend_icons = TRUE
  ) +
  scale_color_manual(values = c(
    "Car"     = "#E64A19",
    "Bicycle" = "#2E7D32",
    "Plane"   = "#1565C0"
  )) +
  theme_pop() +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  scale_legend_icon(size = 8) +
  labs(title = "Tip 1: Valid FA icon names", color = "Transport")
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 2 — Avoid reserved column names

`ggpop` uses several internal column names during layout computation. If your data already contains any of these names, the geom will throw an error:

| Reserved name | Purpose |
|:---|:---|
| `x1` | Computed x position |
| `y1` | Computed y position |
| `pos` | Icon position index |
| `image` | PNG path (internal) |
| `coord_size` | Coordinate scaling |
| `icon_size` | Icon rendering size |
| `icon_stroke_width` | Stroke scaling |
| `alpha` | Icon transparency (internal) |

**Rename any conflicting columns before calling `geom_pop()` or `geom_icon_point()`.**

```{r}
#| label: tip2
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
#| dev: png
#| dev-args: !expr list(bg = "transparent")

# Safe column names — no conflict with internal reserved names
df_tip2 <- data.frame(
  sex      = rep(c("Male", "Female"), each = 20),
  icon     = rep(c("mars", "venus"), each = 20),
  age_grp  = rep(c("Adult", "Child"), times = 20),  # safe name
  stringsAsFactors = FALSE
)

ggplot() +
  geom_pop(
    data = df_tip2,
    aes(icon = icon, color = sex),
    size = 3, dpi = 100, legend_icons = TRUE
  ) +
  scale_color_manual(values = c("Male" = "#1565C0", "Female" = "#C62828")) +
  theme_pop() +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  scale_legend_icon(size = 8) +
  labs(title = "Tip 2: Safe column names", color = "Sex")
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 3 — Use `color`, not `fill`

`geom_pop()` renders icons as raster images. This means:

- `fill` is **not supported** → hard error
- **`color`** is the correct aesthetic for icon color
- **`alpha`** is supported — either as a fixed parameter (`geom_pop(alpha = 0.5)`) or mapped via `aes(alpha = col)`, but **`alpha` is a reserved column name** — rename your column first (e.g. `opacity`)

::: {.callout-important}
## What NOT to do
```r
# fill will error in geom_pop():
aes(icon = icon, group = sex, fill = sex)   # Error
```
:::

```{r}
#| label: tip3
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
#| dev: png
#| dev-args: !expr list(bg = "transparent")

df_tip3 <- data.frame(
  region = rep(c("North", "South", "East", "West"), each = 15),
  icon   = rep(c("compass", "arrow-down", "arrow-right", "arrow-left"), each = 15),
  stringsAsFactors = FALSE
)

ggplot() +
  geom_pop(
    data = df_tip3,
    aes(icon = icon, color = region,  alpha = 0.5),                       # fixed alpha ✓ — works as a 
    size = 3, dpi = 100, legend_icons = TRUE
  ) +
  scale_color_manual(values = c(
    "North" = "#00897B", "South" = "#E64A19",
    "East"  = "#7B1FA2", "West"  = "#F9A825"
  )) +
  theme_pop() +
  scale_legend_icon(size = 8) +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  labs(title = "Tip 3: Use color, not fill", color = "Region")
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 4 — Keep your total icon count at or below 1,000

Max **1,000 icons** per facet panel — exceeding this raises an error. Use `process_data(sample_size = ...)` to stay within limits.

```{r}
#| label: tip4
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
#| dev: png
#| dev-args: !expr list(bg = "transparent")

df_tip4_raw <- data.frame(
  group = c("Group A", "Group B", "Group C"),
  n     = c(4500000, 3200000, 2100000)
)

# process_data samples down to sample_size icons total
df_tip4 <- process_data(
  data        = df_tip4_raw,
  group_var   = group,
  sum_var     = n,
  sample_size = 100          # stays well under the 1,000 limit
) %>%
  mutate(icon = case_when(
    type == "Group A" ~ "circle",
    type == "Group B" ~ "square",
    type == "Group C" ~ "triangle-exclamation"
  ))

ggplot() +
  geom_pop(
    data = df_tip4,
    aes(icon = icon, color = type),
    size = 2, dpi = 100, legend_icons = TRUE
  ) +
  scale_color_manual(values = c(
    "Group A" = "#1565C0",
    "Group B" = "#2E7D32",
    "Group C" = "#E64A19"
  )) +
  theme_pop() +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  scale_legend_icon(size = 8) +
  labs(
    title    = "Tip 4: Use process_data() to control icon count",
    subtitle = "sample_size = 100 — well under the 1,000-icon limit",
    color    = "Group"
  )
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 5 — Don't map `x` or `y` in `geom_pop()`

Don't map `x` or `y` in `aes()` — ggpop computes positions internally and will warn if you do.

::: {.callout-warning}
## This will warn (and x/y are silently ignored)
```r
geom_pop(data = df, aes(icon = icon, group = sex, x = sex, y = sex))
```
:::

```{r}
#| label: tip5
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
#| dev: png
#| dev-args: !expr list(bg = "transparent")

df_tip5 <- data.frame(
  type = rep(c("Urban", "Rural"), each = 25),
  icon = rep(c("building", "tree"), each = 25),
  stringsAsFactors = FALSE
)

# Correct: no x or y in aes() — geom_pop() handles layout automatically
ggplot() +
  geom_pop(
    data = df_tip5,
    aes(icon = icon, color = type),
    size = 3, dpi = 100, legend_icons = TRUE
  ) +
  scale_color_manual(values = c("Urban" = "#5C6BC0", "Rural" = "#388E3C")) +
  theme_pop() +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  scale_legend_icon(size = 8) +
  labs(title = "Tip 5: No x/y mapping needed in geom_pop()", color = "Area")
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 6 — One icon per legend group when using `legend_icons = TRUE`

Each `color` group must map to exactly one icon name when `legend_icons = TRUE`.

```{r}
#| label: tip6
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
#| dev: png
#| dev-args: !expr list(bg = "transparent")


# Each group maps to exactly one icon — clean legend
df_tip6 <- data.frame(
  species = rep(c("Birds", "Fish", "Trees"), each = 20),
  icon    = rep(c("dove", "fish", "tree"), each = 20),
  stringsAsFactors = FALSE
)

ggplot() +
  geom_pop(
    data = df_tip6,
    aes(icon = icon, color = species),
    size = 3, dpi = 100,
    legend_icons = TRUE            # one icon per group ✓ — no warning
  ) +
  scale_color_manual(values = c(
    "Birds" = "#0277BD",
    "Fish"  = "#00897B",
    "Trees" = "#2E7D32"
  )) +
  theme_pop() +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  scale_legend_icon(size = 8) +
  labs(title = "Tip 6: One icon per legend group", color = "Species")
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 7 — `scale_legend_icon()` must come after all theme calls

All `theme()` and `theme_*()` calls must come **before** `scale_legend_icon()` — a theme call after it resets the key size.

::: {.callout-important}
## Wrong order — theme() after scale_legend_icon() resets key size
```r
ggplot(...) +
  geom_pop(...) +
  scale_legend_icon(size = 10) +   # ← scale_legend_icon first
  theme_pop()                       # ← then theme — WRONG
```
:::

```{r}
#| label: tip7
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
#| dev: png
#| dev-args: !expr list(bg = "transparent")

df_tip7 <- data.frame(
  status = rep(c("Active", "Inactive"), each = 25),
  icon   = rep(c("circle-check", "circle-xmark"), each = 25),
  stringsAsFactors = FALSE
)

# Correct order: theme calls BEFORE scale_legend_icon()
ggplot(data = df_tip7,
    aes(icon = icon, color = status)) +
  geom_pop(size = 3, dpi = 100, legend_icons = TRUE) +
  scale_color_manual(values = c("Active" = "#2E7D32", "Inactive" = "#C62828")) +
  theme_pop() +                     # theme first
  theme(legend.position = "bottom") +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  scale_legend_icon(size = 10) +    # scale_legend_icon last
  labs(
    title    = "Tip 7: Correct layer order",
    subtitle = "theme calls → scale_legend_icon()",
    color    = "Status"
  )
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 8 — Use `process_data()` to convert count data

If your data has one row per group with a count column, use `process_data()` to expand it to one row per icon.

```{r}
#| label: tip8
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
#| dev: png
#| dev-args: !expr list(bg = "transparent")

# Your raw count data
df_counts_raw <- data.frame(
  education = c("No degree", "High school", "Bachelor's", "Graduate"),
  population = c(12500000, 38000000, 45000000, 18000000)
)

# Expand to one row per icon
df_edu <- process_data(
  data        = df_counts_raw,
  group_var   = education,
  sum_var     = population,
  sample_size = 100
) %>%
  mutate(icon = case_when(
    type == "No degree"   ~ "xmark",
    type == "High school" ~ "school",
    type == "Bachelor's"  ~ "graduation-cap",
    type == "Graduate"    ~ "user-graduate"
  ))

df_edu$type <- factor(df_edu$type,
  levels = c("No degree", "High school", "Bachelor's", "Graduate"))

ggplot(data = df_edu, aes(icon = icon, color = type)) +
  geom_pop(size = 2, dpi = 100, legend_icons = TRUE, arrange = TRUE) +
  scale_color_manual(values = c(
    "No degree"   = "#B71C1C",
    "High school" = "#E65100",
    "Bachelor's"  = "#1565C0",
    "Graduate"    = "#1B5E20"
  )) +
  theme_pop() +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  scale_legend_icon(size = 6) +
  labs(
    title    = "Tip 8: Use process_data() for count-based data",
    subtitle = "Each icon ≈ 1% of the total population sample",
    color    = "Education"
  )
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 9 — Use `seed` for reproducible charts

Pass `seed` to `geom_pop()` for a reproducible layout — useful in papers, dashboards, or automated pipelines.

::: {.callout-tip}
## Why this matters
If you are including a chart in a paper, dashboard, or automated report, you want the output to be **identical every time** the code runs. A fixed seed guarantees that.
:::

```{r}
#| label: tip9
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
#| dev: png
#| dev-args: !expr list(bg = "transparent")

df_tip9_raw <- data.frame(
  source     = c("Coal", "Natural Gas", "Nuclear", "Renewables"),
  generation = c(800000, 1600000, 700000, 900000)
)

df_tip9 <- process_data(
  data        = df_tip9_raw,
  group_var   = source,
  sum_var     = generation,
  sample_size = 100
) %>%
  mutate(icon = case_when(
    type == "Coal"        ~ "industry",
    type == "Natural Gas" ~ "fire",
    type == "Nuclear"     ~ "atom",
    type == "Renewables"  ~ "sun"
  ))

ggplot(data = df_tip9, aes(icon = icon, color = type)) +
  geom_pop(size = 2, dpi = 100, seed = 42) +
  scale_color_manual(values = c(
    "Coal"        = "#B0BEC5",
    "Natural Gas" = "#FFB74D",
    "Nuclear"     = "#CE93D8",
    "Renewables"  = "#4DB6AC"
  )) +
  theme_pop() +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  scale_legend_icon(size = 8) +
  labs(
    title    = "U.S. Electricity Generation by Source",
    subtitle = "Each icon represents ~1% of total generation — layout fixed with seed = 42",
    color    = "Energy source"
  )
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 10 — Use `arrange = TRUE` to cluster icons by group

Use `arrange = FALSE` (default) for a scattered effect. Use `arrange = TRUE` to cluster icons by group, making boundaries between groups visible.

```{r}
#| label: tip12
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
#| dev: png
#| dev-args: !expr list(bg = "transparent")

df_tip12 <- data.frame(
  outcome = c(rep("Recovered", 65), rep("Ongoing", 25), rep("Worsened", 10)),
  icon    = c(rep("circle-check", 65), rep("arrow-right", 25), rep("circle-xmark", 10)),
  stringsAsFactors = FALSE
)

df_tip12$outcome <- factor(df_tip12$outcome,
  levels = c("Recovered", "Ongoing", "Worsened"))

ggplot(data = df_tip12, aes(icon = icon, color = outcome)) +
  geom_pop(size = 2, dpi = 100, legend_icons = TRUE, arrange = TRUE) +
  scale_color_manual(values = c(
    "Recovered" = "#2E7D32",
    "Ongoing"   = "#F9A825",
    "Worsened"  = "#C62828"
  )) +
  theme_pop() +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  scale_legend_icon(size = 8) +
  labs(
    title    = "Tip 12: arrange = TRUE clusters icons by group",
    subtitle = "Groups appear contiguously — proportional boundaries are clear",
    color    = "Outcome"
  )
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 11 — Per-group alpha: rename the column and hide the alpha legend entry

When you want different transparency per group, follow this three-step workflow:

1. **Rename** your transparency column — `alpha` is a reserved internal name, use `opacity` or any other name
2. **Map** it in `aes()`: `aes(alpha = opacity)`
3. **Suppress** the auto-generated alpha legend with `guides(alpha = "none")` — the color legend already encodes all the information

Skipping step 3 leaves an unwanted legend entry. Skipping step 1 causes an error.

::: {.callout-important}
## What NOT to do
```r
# Error — alpha is a reserved internal column name in ggpop
df$alpha <- c(1.0, 0.6, 0.3)
aes(alpha = alpha)   # Error
```
:::

```{r}
#| label: tip13
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
#| dev: png
#| dev-args: !expr list(bg = "transparent")

df_tip13 <- data.frame(
  status  = c(rep("Confirmed", 60), rep("Probable", 25), rep("Suspected", 15)),
  icon    = c(rep("circle-check", 60), rep("clock", 25), rep("circle-question", 15)),
  opacity = c(rep(1.0, 60), rep(0.6, 25), rep(0.3, 15))  # ← named "opacity", not "alpha"
)

df_tip13$status <- factor(df_tip13$status,
  levels = c("Confirmed", "Probable", "Suspected"))

ggplot(data = df_tip13, aes(icon = icon, color = status, alpha = opacity)) +
  geom_pop(size = 2, dpi = 100, legend_icons = TRUE) +
  scale_color_manual(values = c(
    "Confirmed" = "#1565C0",
    "Probable"  = "#6A1B9A",
    "Suspected" = "#E64A19"
  )) +
  guides(alpha = "none") + #step 3: hide the auto alpha legend
  theme_pop() +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        legend.position = "bottom") +
  scale_legend_icon(size = 8) +
  labs(
    title    = "Tip 13: Per-group alpha — rename column, map it, hide the extra legend",
    subtitle = "opacity → aes(alpha = opacity) + guides(alpha = 'none')",
    color    = "Case status"
  )
```

<div style="line-height: 0.6;"><br></div>

---

## Tip 12 — With `facet_wrap()`, the icon limit applies per panel

`geom_pop()` enforces a maximum of **1,000 icons per facet panel** — not globally. Four panels of 250 icons each (1,000 total) is well within limits; two panels of 1,001 each will error.

Use `high_group_var` in `process_data()` to sample independently per panel and keep `sample_size` low enough that no single panel exceeds the cap. Tell `geom_pop()` which column drives the faceting by passing `facet = group`.

::: {.callout-tip}
## Rule of thumb
Keep `sample_size` ≤ 1,000 ÷ number of panels to leave headroom in every panel.
:::

```{r}
#| label: tip14
#| fig-width: 10
#| fig-height: 10
#| message: false
#| warning: false
#| dev: png
#| dev-args: !expr list(bg = "transparent")

df_tip14_raw <- data.frame(
  region = rep(c("North", "South", "East", "West"), each = 2),
  sex    = rep(c("Male", "Female"), times = 4),
  n      = c(2100000, 1900000, 3200000, 2800000, 1500000, 1400000, 2700000, 2500000)
)

# 50 icons per panel × 4 panels = 200 total — well within the 1,000-per-panel limit
df_tip14 <- process_data(
  data           = df_tip14_raw,
  high_group_var = "region",
  group_var      = sex,
  sum_var        = n,
  sample_size    = 50
) %>%
  mutate(icon = case_when(
    type == "Male"   ~ "mars",
    type == "Female" ~ "venus"
  ))

ggplot(data = df_tip14, aes(icon = icon, color = type)) +
  geom_pop(size = 2, dpi = 100, legend_icons = TRUE, facet = group) +
  facet_wrap(~ group) +
  scale_color_manual(values = c("Male" = "#1565C0", "Female" = "#C62828")) +
  theme_pop() +
  theme(plot.title = element_text(color = "white"),
        plot.subtitle = element_text(color = "white"),
        legend.text = element_text(color = "white"),
        legend.title = element_text(color = "white"),
        strip.text= element_text(color = "white"),
        legend.position = "bottom") +
  scale_legend_icon(size = 8) +
  labs(
    title    = "Tip 14: Facet icon limit is per panel",
    subtitle = "50 icons per panel × 4 panels — each well within the 1,000-per-panel cap",
    color    = "Sex"
  )
```
